---
title: "Analysis_TurnAngle_SpatDisc"
author: "Anna Steel"
date: "November 14, 2016"
output: pdf_document
---

## Turning Angles
Using dataset filtered and discretized by distance, we will calculate the turning angles (only for rel 1&2)

```{r setup, include=FALSE}
# required packages
library(dplyr)
library(sp)
library(rgdal)
library(rgeos)
library(maptools)
library(ggplot2)
library(grid) 
library(cowplot)
library(viridis)
library(adehabitatLT)
library(adehabitatHR)
library(stringr)
library(circular)
library(psych)        # circadian.mean(); circadian.sd()
library(multcomp)     # glht()
library(gridExtra)
library(HH)           # hov()

#source("Functions_General.R")
```

## get data
```{r get data}
  red.r21 <- readRDS("Maestros/RediscSpat_27m.RData")  

   options(digit.secs = 6)
   red.r21$date = as.POSIXct(red.r21$date)     
```

## clean data
```{r clean data, echo=FALSE}
  # remove the last row for every fish
  red.r21 = red.r21[!is.na(red.r21$dist),]

  # add a compass bearing, seperately for quadrant 4 (top left)
  # The way adehabitatLT calculates the absolute angle is with 0 along the positive xaxis, 
  #  with the top of the unit circle as positive values from 0 to 180 and the bottom as negative values from 0 to -180.
  # Thus, the following two lines convert that into compass bearings
  red.r21$compass.angle[red.r21$abs.angle<=rad(90)] <- 90 + (-1)*deg(red.r21$abs.angle[red.r21$abs.angle<=rad(90)] )
  red.r21$compass.angle[red.r21$abs.angle>rad(90) ] <- 360 - ( deg(red.r21$abs.angle[red.r21$abs.angle>rad(90)   ]) - 90 )
  
  # and convert 'rel.angle' which is measured in radians to 'rel.deg' which is measured in degrees (-180 to 180)
   red.r21$rel.deg = deg(red.r21$rel.angle)
```


## mean bearings and turning angles  - unsure if this is correct! Check conversion to bearings wth mo's for-loop and function ('bearing()')
```{r means, echo=TRUE}

## Calculate mean bearings and turn angles for each fish so we can use standard statistics on independent samples (one per fish)
   red.r21 = red.r21[order(red.r21$id, red.r21$date),]
   red.indivmn = as.data.frame(summarise(group_by(red.r21, id, RelEv, RelHr, FL, weight), 
          mn.bearing=as.numeric(mean.circular(circular(compass.angle, units="degrees"))),  # use circular statistic here
          mn.turndeg=as.numeric(mean(abs(rel.deg), na.rm=T)),  # because these are +/- values from straight, use arithmetic mean of abs values
          firstdate = date[1],
          arriv.stgft = stage_ft[1],
          mn.stgft = as.numeric(mean(stage_ft))))
   #trash = group_by(red.r21, id) %>% slice(1) %>% data.frame() # check that the prev is working correctly
   
   red.indivmn$inv.mn.turndeg = 1/red.indivmn$mn.turndeg
   
  ##  Look at normality and heterogeneity of variance
    # check for homogeneitry of var for subsequent ANOVA
      bartlett.test(red.indivmn$mn.turndeg~red.indivmn$RelEv)
        # Bartlett's K-squared = .38811, p=0.533
  
    # check for ~N
      #windows()
       qqnorm(red.indivmn$mn.turndeg/60)
       qqline(red.indivmn$mn.turndeg/60)
         # not perfect but not tooo bad
       
      
      # From Lix et al 1996, the Welch test is the least sensitive (in terms of type 1 error) to skew/kurtosis and heterogeneity of variance
      #  but this is still a parametric test that compares means (assumes means describe the distribution)
      #   pt.Welch.aov = oneway.test(red.indivmn$mn.turndeg ~ factor(red.indivmn$RelEv))
      #      # F = 29.166, num df = 1, denom df = 427.53, p-value = 0.0000001104
      #   library(userfriendlyscience)
      #    posthocTGH(y=red.indivmn$mn.turndeg, x=factor(red.indivmn$RelEv)  )
       
      # t.test
   t.test(red.indivmn$mn.turndeg~red.indivmn$RelEv) 
```

```{r plots}
   # all fish together
  ggplot(red.indivmn, aes(y=mn.turndeg, x=1)) + 
    geom_boxplot() + ylab("Mean Turning Angle") +
     theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
  
   #  by release event:
   tdeg.relev = ggplot(data=red.indivmn, aes(y=mn.turndeg, x=factor(RelEv))) + 
     geom_boxplot() + xlab("Release Event") + ylab("Mean Turning Angle")
   tdeg.relev
   
   png("Graphics/TDeg_by_RelEv.png", width=4, height=4, unit="in", res=600)
     tdeg.relev
   dev.off()
      
   
   ggplot(data=red.indivmn, aes(x=mn.turndeg, group=factor(RelEv), fill=factor(RelEv))) +
     geom_histogram(alpha=0.5, position="identity", binwidth=1, color="black") + 
     scale_fill_discrete(name="Release\nEvent") + xlab("Mean Turning Angle")
   
  # by release hour
   ggplot(data=red.indivmn, aes(x=factor(RelHr), y=mn.turndeg)) + 
    geom_boxplot() + xlab("Hour of Release") + ylab("Mean Turning Angle")
   
  # by mean River stage
   tdeg.stg = ggplot(red.indivmn, aes(y=mn.turndeg, x=mn.stgft, colour=factor(RelEv))) + 
    geom_point(pch=16, cex=4) +
    xlab("Mean River Stage (ft)") + ylab("Mean Turning Angle") + 
    ggtitle("Mean Track Turning Angle by River Stage") + scale_colour_discrete(name="Release\nEvent")
   tdeg.stg
   
  png("Graphics/TDeg_by_Stage.png", width=6, height=4, unit="in", res=600)
   tdeg.stg
  dev.off()
  
```      



```{r full model}
   omega = 2*pi/24
    cosrelhr = cos(omega*red.indivmn$RelHr)
    sinrelhr = sin(omega*red.indivmn$RelHr)
      
    # This uses true release events, not the arrival groups. 
    
  fullmod = lm(inv.mn.turndeg ~ factor(RelEv)+arriv.stgft + sinrelhr + cosrelhr, data=red.indivmn)
    summary(fullmod)
          
  intmod = lm(inv.mn.turndeg ~ factor(RelEv)*arriv.stgft + sinrelhr + cosrelhr, data=red.indivmn)
    summary(intmod)
    
  norelevmod = lm(inv.mn.turndeg ~ arriv.stgft + sinrelhr + cosrelhr, data=red.indivmn)
    summary(norelevmod)  
    
  arrivmod = lm(inv.mn.turndeg ~ factor(RelEv) + arriv.stgft + sinrelhr + cosrelhr, data=red.indivmn)
    summary(arrivmod)
```  



## read in and run 2015 data for comparision  -  spent lots of time getting stage onto 15 dataset, and didn't need to in the end!! Geesh, Anna 
```{r comp2015, echo=FALSE}
  # read in speed data - long way around the barn to get mean stages to go with mean bearings
  red15 <- read.csv("C:/Users/Anna/Documents/03_SacBankUSACE/FremontWeir/DATA-output/TrajectoryTagging_Filtered39ExtraFish_TempDisc20sec_Staggered.csv")
 
   options(digit.secs = 6)
   red15$date = as.POSIXct(red15$date, tz="Etc/GMT-8") 
  
   # read in stage data  
  fre2015 = read.csv("C:/Users/Anna/Documents/03_SacBankUSACE/FremontWeir/DATA/CDEC_FRE_stage.csv")
  names(fre2015) = c("datePST","timePST","stage_ft")
  
  fre2015 = fre2015[!is.na(fre2015$stage_ft),]
     fre2015$timePST = str_pad(fre2015$timePST, 4, pad = "0")
     fre2015$datetimePST = as.POSIXct(paste(fre2015$datePST, fre2015$timePST), format="%Y%m%d %H%M", tz="Etc/GMT-8")
     fre2015$datetimeUTC = as.POSIXct(as.character(fre2015$datetimePST + (60*60*8)), tz="GMT")
     fre2015 = fre2015[order(fre2015$datetimePST),]
     fre2015$stageid = rownames(fre2015)
     
  red15$RelIndex <- 
     findInterval( red15$date, c(-Inf, head(fre2015$datetimePST,-1))+ c(0,diff(as.numeric(fre2015$datetimePST))/2 )) 
  
  red15 = merge(red15, fre2015[,c("stage_ft", "datetimePST","stageid")], by.y="stageid", by.x="RelIndex", all.x=T)
 
  mnStg15 = summarize(group_by(red15,id),
                          first=min(date), 
                          arriv.stg = stage_ft[1],
                          mnStg = mean(stage_ft))
    mnStg15 = data.frame(mnStg15)

    # read in mean bearing dataset 
    red.indivmn15 = readRDS("C:/Users/Anna/Documents/03_SacBankUSACE/FremontWeir/DATA-output/mn_turnangles.csv")
  
  # remove scout fish
  mnStg15 = mnStg15[mnStg15$id!=51099,]

  # merge mean stage onto mean bearings
  red.indivmn15 = merge(red.indivmn15, mnStg15, by="id")

```


