---
title: "Analysis_MovSpd_TempDisc"
author: "Anna Steel"
date: "November 3, 2016"
output: pdf_document
---

```{r startup, include=FALSE} 
# required packages
library(dplyr)
library(sp)
library(rgdal)
library(rgeos)
library(maptools)
library(ggplot2)
library(grid) 
library(cowplot)
library(viridis)
library(adehabitatLT)
library(adehabitatHR)
library(stringr)
library(circular)
library(psych)        # circadian.mean(); circadian.sd()
library(multcomp)     # glht()
#library(userfriendlyscience)

river3 = readOGR("C:/Users/Anna/Documents/GitHub/Fremont16/GIS/2004_channel","2004_channel_freTightclip")

```

## Movement Speed (mean spd per track)
Using the dataset filtered and discretized by time, we'll calculate the mean movement speed per track
```{r get data, echo=FALSE}
  red2 <- readRDS("Maestros/RediscTime_20sNoGapFish.RData")  

   options(digit.secs = 6)
   red2$date = as.POSIXct(red2$date)     
```

Visualize with a variety of plots
```{r plot raw data, include=FALSE}

       # plot all tracks as lattice in a pdf
       # pdf("Graphics/Tracks_tempredisc_20sec_Staggered.pdf", width=8, height=10.5)
       #   lapply(seq(from=24, to=480, by=24), function(x) {plot.ltraj(dl(red2)[(x-23):x])})
       # dev.off()
              
       # plot speeds by size
        #   windows()
        #   plot(red2$spd_mps ~ red2$Weight)
        #    abline(lm(red2$spd_mps ~ red2$Weight), col="red")
        #   plot(red2$spd_mps ~ red2$FL, xlab="Fork Length", ylab="Ground Speed (mps)", main="Both runs combined")
        #    abline(lm(red2$spd_mps ~ red2$FL), col="red")
        #           #  abline(lm(red2$spd_mps[red2$run=="LFC"] ~ red2$FL[red2$run=="LFC"]), col="green3") 
        #           #  abline(lm(red2$spd_mps[red2$run=="WRC"] ~ red2$FL[red2$run=="WRC"]), col="cyan2")
        #           #   points(red2$spd_mps[red2$run=="WRC"] ~ red2$FL[red2$run=="WRC"], col="cyan4")
    
        #  summary(lm(red2$spd_mps ~ red2$FL))
        #  summary(lm(red2$spd_mps ~ red2$FL))
    
       # plot a few simple scatterplots with spatial elements
        #   windows()
        #     plot(red2$spd_mps ~ red2$x) 
        #     plot(red2$y ~ red2$spd_mps)
        #     plot(red2$spd_mps ~ red2$dx)
        #     plot(red2$dy ~ red2$spd_mps)
            
      # plot tracks with points color-coded for speed 
        #           spdmap2 = ggplot(data=red2, aes(x=x, y=y, colour=spd_mps)) + geom_point() + scale_colour_gradientn(colours=rainbow(7)) 
        #            windows(); spdmap2

```


## Calculate overall path speeds
Using path length and passage time
```{r mean spd, echo=FALSE}
   red2 = red2[order(red2$id, red2$date),]
   pathspd = summarize(group_by(red2,id),
                       pathlength_m = round(sum(dist, na.rm=T),1), 
                       first = min(date), last = max(date), 
                       RelHr = unique(RelHr), RelEv = unique(RelEv), 
                       mnStg = mean(stage_ft),
                       stage_arrival = stage_ft[1],
                       FL = unique(FL), weight = unique(weight))

    pathspd = data.frame(pathspd)
    pathspd$passagetime_s = as.numeric(difftime(pathspd$last, pathspd$first, units="sec"))
    pathspd$mps = pathspd$pathlength_m / pathspd$passagetime_s
    
    pathspd$grp = NA
     pathspd$grp[pathspd$first<as.POSIXct("2016-03-05")] <- 1
     pathspd$grp[pathspd$first>as.POSIXct("2016-03-05")] <- 2  # moves two fish from relev 1 to grp 2: id=36382 & 36597
     
    pathspd$diel = NA
     pathspd$diel[pathspd$RelHr %in% c(3,5,21,23)] <- "night"
     pathspd$diel[pathspd$RelHr %in% c(8,10,14,16,17)] <- "day"     
```

## Plot all speeds
```{r plot spds, echo=FALSE}
  # plot speed for all fish
  # windows(3.5,4); par(mar=c(5,5.5,4,4))
  ggplot(data=pathspd, aes(y=mps, x=1)) + geom_boxplot() + ylab("Ground Speed (mps)") +
     theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
 
  # plot speed by RelHr
  #windows(5,5); par(mar=c(5,5.5,4,4))
  ggplot(data=pathspd, aes(x=factor(RelHr), y=mps)) + 
    geom_boxplot() + xlab("Hour of Release") + ylab("Ground Speed (mps)")
  
  # plot speed by Diel Phase
  #windows(5,5); par(mar=c(5,5.5,4,4))
  ggplot(data=pathspd, aes(x=factor(diel), y=mps)) + 
    geom_boxplot() + xlab("Diel Phase of Release") + ylab("Ground Speed (mps)")
   
   
  ## plot speed by arrival grp
  sog.relev = ggplot(data=pathspd, aes(x=factor(grp), y=mps)) + 
    geom_boxplot() + xlab("Arrival Group (2016)") + ylab("Mean track speed (mps)")
  sog.relev
  
   png("Graphics/SoG_by_RelEv.png", width=4, height=4, unit="in", res=600)
     sog.relev
   dev.off()
 
 ggplot(data=pathspd, aes(x=mps, group=factor(grp), fill=factor(grp))) + 
   geom_histogram(alpha=0.5, position="identity", binwidth=.1, color="black") +
   scale_fill_discrete(name="Arrival\nGroup")

  ## plot speed by mean river stage experienced during the track
  sog.stg = ggplot(pathspd, aes(y=mps, x=stage_arrival)) + 
    geom_point(pch=16, cex=4, aes(colour=factor(RelEv))) +
    geom_smooth(method=lm, col="grey40", se=F, lty=2) + 
    xlab("River Stage upon Arrival (ft)") + ylab("Mean track speed (mps)") + 
    ggtitle("Reach-scale Ground Speed by River Stage") + scale_colour_discrete(name="Release\nEvent")
  sog.stg

   png("Graphics/SoG_by_Stg.png", width=6, height=4, unit="in", res=600)
     sog.stg
   dev.off()
```

## Statistical effect of release hour alone
There is a significant effect of release hour, both then it is considered as a continuous variable and as a factor, but the models and the plots indicate that the effect is very small. We will include the release hour as a mixed effect in future models, but because there is such a huge spread in release hours we won't analyze these groups seperately. 
```{r RelHr vs spd, echo=TRUE}
  mps.RelHr <- lm(mps ~ (RelHr), data=pathspd)  
   summary(mps.RelHr) 
   #plot(mps.RelHr)  # meets assumptions just fine! 
   
   # post-hoc test designed for linear models with factor predictor: multcomp::glht() was recommended
     pathspd$RelHrfac = factor(pathspd$RelHr)
     testmod = lm(mps ~ 0+RelHrfac, data = pathspd)
      summary(testmod)
     posthoc.mod = glht(testmod, linfct = mcp(RelHrfac="Tukey"))
      summary(posthoc.mod)
 
     boxplot(mps ~ RelHrfac, data = pathspd)
```   


## Statistical effect of release event alone
Release Events 1,2&3 are not significantly different from one another, nor are 4 and 5 significantly different from one another, but the two groups (1,2,3 vs 4,5) are different. This make sense, as 1,2 and 3 were released before over topping, and 4 and 5 were during the overtopping event. 

```{r RelEv vs spd, echo=TRUE,eval=FALSE}
  mps.RelEv <- lm(mps ~ RelEv, data=pathspd)  
   summary(mps.RelEv) 
   #plot(mps.RelEv)  # meets assumptions pretty well? 
   
   # as an anova test, with tukey posthoc test
  #   testmod = aov(mps ~ 0+RelEvfac, data = pathspd)
  #    summary(testmod)
  #   TukeyHSD(testmod)
   pathspd$RelEvfac = factor(pathspd$RelEv)
   t.test(mps ~ 0+RelEvfac, data = pathspd)
    summarize(group_by(pathspd, RelEvfac), mean(mps, na.rm=T), sd(mps, na.rm=T))
   
   boxplot(mps ~ RelEvfac, data = pathspd, ylab="Mean Track Speed (mps)", xlab="ReleaseEvent")
   
   
   # phase 2: re-assign the two fish from the first release that arrived with the second release
   pathspd$grp <- NA
    pathspd[pathspd$first < as.POSIXct("2016-03-02"),"grp"] <- 1
    pathspd[pathspd$first > as.POSIXct("2016-03-02"),"grp"] <- 2
    pathspd$grp = factor(pathspd$grp)
    
  mps.Grp <- lm(mps ~ grp, data=pathspd)  
   summary(mps.Grp) 
 
   t.test(mps ~ 0+grp, data = pathspd)
    summarize(group_by(pathspd, grp), mean(mps, na.rm=T), sd(mps, na.rm=T))
   
   boxplot(mps ~ grp, data = pathspd, ylab="Mean Track Speed (mps)", xlab="Arrival Group")
```   
   
## River Stage upon Arrival
```{r river stage, echo=FALSE}
  # by release event
    data.frame(  summarize(group_by(pathspd, RelEv), med.stage = median(stage_arrival, na.rm=T), mn.stage = mean(stage_arrival, na.rm=T), sd.stage=sd(stage_arrival, na.rm=T), min.stage = min(stage_arrival, na.rm=T), max.stage = max(stage_arrival, na.rm=T)))

  # by group (2 fish from rel 1 lumped in with rel2)
      data.frame(  summarize(group_by(pathspd, grp), med.stage = median(stage_arrival, na.rm=T), mn.stage = mean(stage_arrival, na.rm=T), sd.stage=sd(stage_arrival, na.rm=T), min.stage = min(stage_arrival, na.rm=T), max.stage = max(stage_arrival, na.rm=T)))

       
  # SacRiver Stage - pulled from CDEC - ask for QAQC data from DWR if this seems okay 
    frestg = read.csv("C:/Users/Anna/Documents/GitHub/Fremont16/Maestros/FRE_stage_2016study.csv")
    frestg = frestg[!is.na(frestg$stage_ft),]
    frestg = frestg[frestg$stage_ft > 5 ,] # some missing values are recorded as 2 or 5; remove these entirely
     frestg$timePST = str_pad(frestg$timePST, 4, pad = "0")
     frestg$datetimePST = as.POSIXct(paste(frestg$datePST, frestg$timePST), format="%Y%m%d %H%M", tz="Etc/GMT-8")
     frestg$datetimeUTC = as.POSIXct(as.character(frestg$datetimePST + (60*60*8)), tz="GMT")
     frestg = frestg[order(frestg$datetimePST),]
     frestg$stageid = rownames(frestg)

  pathspd2 = pathspd
  pathspd2$RelIndex <- 
     findInterval( pathspd2$first, c(-Inf, head(frestg$datetimePST,-1))+ c(0,diff(as.numeric(frestg$datetimePST))/2 )) 

  
   mn.total.stg16 = mean(red2$stage_ft)
   sd.total.stg16 = sd(red2$stage_ft)
      mn.total.stg16; sd.total.stg16
      
#   # calculate mean of the mn stage estimates per individual
#   print(paste("mean stage experienced 2016 (ie: mean of stages corresponding to all positions) =", mean(pathspd$mnStg, na.rm=T)))
#   print(paste("sd stage experienced 2016 (ie: sd of stages corresponding to all positions) =", sd(pathspd$mnStg, na.rm=T)))
  
  
  hg = ggplot(frestg, aes(x=datetimePST, y=stage_ft)) + 
     geom_line() + geom_hline(aes(yintercept=33.5), lty=2) +
     geom_point(data=pathspd, aes(x=first, y=stage_arrival, col=factor(RelEv)), pch=16, cex=6) + 
     ggtitle("Arrival times by river stage at Fremont Weir \n(cdec gauge)") + 
     xlab("Date (PST)") + ylab("River Stage (ft)") + 
     scale_colour_manual(name = "Release\nEvent", values =viridis(2), labels = c(1:2))

   hg
   
  png("Graphics/Arrival_Hydrograph.png", width=8, height=4, unit="in", res=600)
   hg
  dev.off()
   
``` 

# build linear model to combine river stage, release event, and release hour (circular)
```{r final model}
  omega = 2*pi/24
   cosrelhr = cos(omega*pathspd$RelHr)
   sinrelhr = sin(omega*pathspd$RelHr)
      
  fullmod = lm(mps ~ factor(grp) + sinrelhr + cosrelhr + mnStg, data=pathspd)
  #  summary(fullmod)
  # plot(fullmod)  # meets assumptions well enough to be trusted
    
  fullmod.a = lm(mps ~ factor(grp) + sinrelhr + cosrelhr + stage_arrival, data=pathspd)
  #  summary(fullmod.a)
  # plot(fullmod)  # meets assumptions well enough to be trusted
    
  dielmod = lm(mps ~ factor(grp) + diel + mnStg, data=pathspd)
  #  summary(dielmod)    
    
  dielmod.a = lm(mps ~ factor(grp) + diel + stage_arrival, data=pathspd)
  #  summary(dielmod.a)    
    
  source("format_lmoutput.R")  
    ci.table(fullmod.a)
```

## read in and run 2015 data for comparision
```{r comp2015, echo=FALSE}
  red15 <- read.csv("C:/Users/Anna/Documents/03_SacBankUSACE/FremontWeir/DATA-output/TrajectoryTagging_Filtered39ExtraFish_TempDisc20sec_Staggered.csv")  # with staggered the start point

   options(digit.secs = 6)
   red15$date = as.POSIXct(red15$date, tz="Etc/GMT-8") 
   
  # read in stage data  
  fre2015 = read.csv("C:/Users/Anna/Documents/03_SacBankUSACE/FremontWeir/DATA/CDEC_FRE_stage.csv")
  names(fre2015) = c("datePST","timePST","stage_ft")
  
  fre2015 = fre2015[!is.na(fre2015$stage_ft),]
     fre2015$timePST = str_pad(fre2015$timePST, 4, pad = "0")
     fre2015$datetimePST = as.POSIXct(paste(fre2015$datePST, fre2015$timePST), format="%Y%m%d %H%M", tz="Etc/GMT-8")
     fre2015$datetimeUTC = as.POSIXct(as.character(fre2015$datetimePST + (60*60*8)), tz="GMT")
     fre2015 = fre2015[order(fre2015$datetimePST),]
     fre2015$stageid = rownames(fre2015)
     
  red15$RelIndex <- 
     findInterval( red15$date, c(-Inf, head(fre2015$datetimePST,-1))+ c(0,diff(as.numeric(fre2015$datetimePST))/2 )) 
  
  red15 = merge(red15, fre2015[,c("stage_ft", "datetimePST","stageid")], by.y="stageid", by.x="RelIndex", all.x=T)
 
  pathspd15 = summarize(group_by(red15,id),
                          pathlength_m = round(sum(dist, na.rm=T),1), 
                          first=min(date), last= max(date), 
                          FL = unique(FL), weight = unique(Weight), 
                          mnStg = mean(stage_ft),
                          stage_arrival = stage_ft[1],
                          run=unique(run), RelHr = unique(RelHr))
    pathspd15 = data.frame(pathspd15)

    pathspd15$passagetime_s = as.numeric(difftime(pathspd15$last, pathspd15$first, units="sec"))
    pathspd15$mps = pathspd15$pathlength_m / pathspd15$passagetime_s

  # remove scout fish
  pathspd15 = pathspd15[pathspd15$id!=51099,]

      
   mn.total.stg15 = mean(red15$stage_ft)
   sd.total.stg15 = sd(red15$stage_ft)
      mn.total.stg15; sd.total.stg15
  
#   # calculate mean of the mn stage estimates per individual
#   print(paste("mean stage experienced 2015 (ie: mean of stages corresponding to all positions) =", mean(pathspd15$mnStg, na.rm=T)))
#   print(paste("sd stage experienced 2015 (ie: sd of stages corresponding to all positions) =", sd(pathspd15$mnStg, na.rm=T)))

```

## Plot simple year comparisons
```{r plot yr comp, echo=FALSE}
   ps15min = pathspd15[,c("id","mps")]
   ps15min$year="2015"

   ps16min = pathspd[,c("id","mps")]
   ps16min$year="2016"   
   
   psyr = rbind(ps15min, ps16min)

   sog.yrcomp = ggplot(data=psyr, aes(y=mps, x=year)) + geom_boxplot() + ylab("Mean track speed (mps)")
   sog.yrcomp
   
   png("Graphics/SoG_by_year.png", width=4, height=4, unit="in", res=600)
     sog.yrcomp
   dev.off()
   
   t.test(psyr$mps ~ psyr$year)
   summarize(group_by(psyr, year), mean(mps), sd(mps))

```  

