---
title: "Kernel UDs 2016"
author: "Anna Steel"
date: "October 19, 2016"
output: pdf_document
---

```{r, include=FALSE} 
# required packages
library(dplyr)
library(sp)
library(rgdal)
library(rgeos)
library(maptools)
library(ggplot2)
library(grid) 
library(cowplot)
library(viridis)
library(adehabitatLT)
library(adehabitatHR)
library(raster)
library(stringr)
#library(userfriendlyscience)

river3 = readOGR("C:/Users/Anna/Documents/GitHub/Fremont16/GIS/2004_channel","2004_channel_freTightclip")
map.proj = CRS(river3@proj4string@projargs)
```

# Kernel Utilization Distributions
### This script uses the temporally rediscretized dataset (currently only 20 sec steps) to create utilization distributions. Here I compare the 2016 data with the 2015 data for LFC - I excluded the WRC for coding simplicity, not scientific reasons. Utiltimately I plan to also consider variability in flow and fish size, but have not yet incorporated those additional variables. 

__________________

## Create kernel UD from tracks
The fish positions are only those from the first two phases - includes 374 individuals (no individuals with tracks containing a >150m of gap between consecutive positions). 

In 2015 the grid was automated to 10.03m squares, with a smoothing parameter h=3.03. The kernelUD() function in adehabitatLT gives options for how to select a smoothing parameter for the bivariate normal probability space defined at each recorded fish position. In 2015 I used the least squares cross validation to select an appropriate value for h (smoothing parameter) - the algorithm looks for a value of the smoothing parameter (h) where the CV(h) is minimized. In 2015 the value selected for h for LFC was 3.03 (some stochasticity in this, changes slightly by run). _For 2016 I set the grid to 10m exactly._ I ran the kernelUD() function with both lscv and href [the ad hoc method of smoother selection, which is h = Sigma*n^(1/6)] approaches to estimating the smoothing parameter, as well as setting it to match the 2015 analysis (h=3.03). The LSCV method for 2016 estimated a smoothing parameter of 3.09, so for consistency sake I adjusted this to 3.03 to be in accordance with the smoother used for 2015. 


## Read in RData object from 2015
```{r kud15, echo=FALSE}
      kud15 <- readRDS("Maestros/kud15_final.RData")
        vud15 = getvolumeUD(kud15)
      # windows(width=4, height=4)
        image(vud15[[1]], col=c(heat.colors(6),"white"), main="LFC 2015")
        xyz.15 <- as.image.SpatialGridDataFrame(vud15[[1]])
        contour(xyz.15, add=TRUE, nlevels=6, drawlabels=FALSE)
      print(paste("smoothing parameter h, lscv; 2015-LFC = ",round(kud15$LFC@h$h,3)))
      
  # save grid to reference for 2016 UD
  #  grid15 = SpatialPixels(SpatialPoints(kud15[[1]]@grid ))
      
```

## Estimate Kernel UD for 2016 using three methods for setting the smoothing parameter
Here I used LSCV (as noted above), href (also as noted above), and a set value of h=3.03 as was selected by lscv in 2015. 
```{r kud 16 all fish, echo=FALSE}
  # create kud/vud for 2016
    red8.trdz = readRDS("Maestros/RediscTime_20sNoGapFishStaggered.RData")

  # create an even 4x4m grid for 2016 -> to match Aaron's selection
    e = extent(615430, 615430+(61*10), 4290820, 4290820+(47*10))
    r = raster(e)
    res(r) = c(4,4)   
    projection(r) = map.proj 
    grid4 = SpatialPixels(SpatialPoints(coordinates(r)))    
    
  
  #  add proper projection
    red8.grp = data.frame(grp=red8.trdz[,"run"])
     xytsp = (red8.trdz[,c("x","y")])
     coordinates(red8.grp) <- xytsp 
     proj4string(red8.grp) <- CRS("+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

  # create kud using lscv and save to file   
    #kud16.lscv_g4 = kernelUD(red8.grp[,1], h="LSCV", kern="bivnorm", extent=0.1, grid=grid4)
       # computationally intensive
    # saveRDS(kud16.lscv_g4, "Maestros/kud16_lscv_stag_4x4.RData")
     
  # read in kud with lscv method   
     kud16.lscv = readRDS("Maestros/kud16_lscv_stag_4x4.RData")  #
      print(paste0("smoothing parameter h, lscv; 2016-LFC = ",round(kud16.lscv$LFC@h$h,3)))  ## h=3.438

    # windows()
    #   plotLSCV(kud16.lscv)
  
  # create kud with href and set h value         
    kud16.href = kernelUD(red8.grp[,1], h="href", kern="bivnorm", extent=0.1, grid=grid4)    
     print(paste0("smothing parameter h, href; 2016-LFC = ",round(kud16.href$LFC@h$h,3)))
     
    kud16.h15 = kernelUD(red8.grp[,1], h=3.03, kern="bivnorm", extent=0.1, grid=grid4) 

    kud16 = kud16.h15
```

## Convert kernel UDs into volume UDs for plotting
```{r plot 16 smoother, echo=FALSE, fig.height=4, fig.width=8}        
      vud16.h15 <- getvolumeUD(kud16.h15) 
       xyz.h15 <- as.image.SpatialGridDataFrame(vud16.h15[[1]])

  vud16 = vud16.h15 
   xyz.16 <- as.image.SpatialGridDataFrame(vud16[[1]])
```

__________________________________
 
## Compare 2016 UD (all fish) with 2015 UD (for 2015-LFC)
```{r comp contour 15 16, echo=FALSE, fig.height=4, fig.width=8}
#   # heatmap
#   png("Graphics/kernelUD_heatmap1516.png", width=10, height=3, units="in", res=600)
#       par(mfrow=c(1,2))
#      image(vud15[[1]], col=c(heat.colors(6),"white"), main="LFC 2015; h=3.03")
#       contour(xyz.15, add=TRUE, nlevels=6, drawlabels=FALSE)  
#          plot(river3, add=T, col="grey60")
#      image(vud16.h15[[1]], col=c(heat.colors(6),"white"), main="LFC 2016; h=3.03")
#       contour(xyz.16, add=TRUE, nlevels=6, drawlabels=FALSE)  
#          plot(river3, add=T, col="grey60")
#   dev.off()
#   
#   # pverlaid contours
#   png("Graphics/kernelUD_contours1516.png", width=10, height=3, units="in", res=600)
#    par(mfrow=c(1,3))
#      contour(xyz.15, add=FALSE, nlevels=5, levels=25, drawlabels=FALSE, lwd=2.5, col="red", main="25% contour")
#      contour(xyz.16, add=TRUE, nlevels=5, levels=25, drawlabels=FALSE, lwd=2.5, col="steelblue2")
#       plot(river3, add=T, col="grey60")
#      legend("topleft", legend=c("2015","2016"), fill=c("red","steelblue2"))
#      contour(xyz.15, add=FALSE, nlevels=5, levels=50, drawlabels=FALSE, lwd=2.5,col="red", main="50% contour")
#       plot(river3, add=T, col="grey60")
#      contour(xyz.16, add=TRUE, nlevels=5, levels=50, drawlabels=FALSE, lwd=2.5,col="steelblue2")
#      contour(xyz.15, add=FALSE, nlevels=5, levels=75, drawlabels=FALSE, lwd=2.5,col="red", main="75% contour")
#      contour(xyz.16, add=TRUE, nlevels=5, levels=75, drawlabels=FALSE, lwd=2.5,col="steelblue2")
#       plot(river3, add=T, col="grey60")
#   dev.off()
```

## Compare similar flows (low flows) across years
In 2015 the river stage was at nearly 15 ft during all releases. In 2016 there was much more variability, with stages ranging from 16.3 to 31.12. Fish from release 1 passed at slightly lower flows, with a median stage of 18.4 ft and a max stage of 27.4 ft. 

## Summary of the flows experienced by each release group
```{r kud 16 by release, echo=FALSE} 

   # assign covariate groups to dataset
      # red8.trdz$grp = red8.trdz$RelEv
      #  red8.trdz$grp[red8.trdz$id==36597] <- 2 
      #  red8.trdz$grp[red8.trdz$id==36382] <- 2
   red8.trdz$grp = NA
    red8.trdz$grp[red8.trdz$stage_ft<20.99+1.95] <- 1  # USGS temp gage is -1.95 off from old CDEC gage; 20.99ft (USGS temp) is cut-off for low-water group, which is equivalent of 22.94 on old CDEC
    red8.trdz$grp[red8.trdz$stage_ft>21.00+1.95] <- 2
    ## perfect match for release events, interstingly enough. 
    
  print(data.frame(summarize(group_by(red8.trdz, grp), mn.stg=mean(stage_ft), sd.stg=sd(stage_ft), max.stg=max(stage_ft), min.stg=min(stage_ft), nfish=length(unique(id)))))
     
     redgrp1 = data.frame(grp=red8.trdz[red8.trdz$grp==1,"run"])
     xytsp.1 = (red8.trdz[red8.trdz$grp==1,c("x","y")])
     coordinates(redgrp1) <- xytsp.1
     proj4string(redgrp1) <- CRS("+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

     redgrp2 = data.frame(grp=red8.trdz[red8.trdz$grp==2,"run"])
     xytsp.2 = (red8.trdz[red8.trdz$grp==2,c("x","y")])
     coordinates(redgrp2) <- xytsp.2
     proj4string(redgrp2) <- CRS("+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

    kud16.g1 = kernelUD(redgrp1[,1], h=3.03, kern="bivnorm", extent=0.1, grid=grid4) # set same as lscv, 2015
     vud16.g1 <- getvolumeUD(kud16.g1) 
     xyz.g1.16 <- as.image.SpatialGridDataFrame(vud16.g1[[1]])

    kud16.g2 = kernelUD(redgrp2[,1], h=3.03, kern="bivnorm", extent=0.1, grid=grid4) # set same as lscv, 2015
     vud16.g2 <- getvolumeUD(kud16.g2) 
     xyz.g2.16 <- as.image.SpatialGridDataFrame(vud16.g2[[1]])
```


## Plots of UD at similar flows (2015 vs 2016-rel1) - heat maps & overlaid contours
```{r plot by release, echo=FALSE, fig.height=4, fig.width=6}
    # heatmap of 2015 vs 2016-rel1 
   #png("Graphics/kernelUD_heatmap1516grp1.png", width=7, height=4, units="in", res=600)     
    par(mfrow=c(1,2))
     image(vud15[[1]], col=c(heat.colors(6),"white"), main="LFC 2015; h=3.03")
      contour(xyz.15, add=TRUE, nlevels=6, drawlabels=FALSE)
            plot(river3, add=T, col="grey60")
     image(vud16.g1[[1]], col=c(heat.colors(6),"white"), main="LFC 2016, rel1; h=3.03")
      contour(xyz.g1.16, add=TRUE, nlevels=6, drawlabels=FALSE)  
                  plot(river3, add=T, col="grey60")
   #dev.off()
   
   # overlaid contours
  #  png("Graphics/kernelUD_contours1516grp1.png", width=10, height=3, units="in", res=600)
     par(mfrow=c(1,3))
       contour(xyz.15, add=FALSE, nlevels=5, levels=25, drawlabels=FALSE, lwd=2.5, col="red", main="25% contour")
       contour(xyz.g1.16, add=TRUE, nlevels=5, levels=25, drawlabels=FALSE, lwd=2.5, col="steelblue2")
        plot(river3, add=T, col="grey60")
       legend("topleft", legend=c("2015","2016-grp1"), fill=c("red","steelblue2"))
       contour(xyz.15, add=FALSE, nlevels=5, levels=50, drawlabels=FALSE, lwd=2.5,col="red", main="50% contour")
        plot(river3, add=T, col="grey60")
       contour(xyz.g1.16, add=TRUE, nlevels=5, levels=50, drawlabels=FALSE, lwd=2.5,col="steelblue2")
       contour(xyz.15, add=FALSE, nlevels=5, levels=75, drawlabels=FALSE, lwd=2.5,col="red", main="75% contour")
       contour(xyz.g1.16, add=TRUE, nlevels=5, levels=75, drawlabels=FALSE, lwd=2.5,col="steelblue2")
        plot(river3, add=T, col="grey60")
   # dev.off()
   
```


## Compare 2016-grp1 UD with 2016-grp2 UD - heat maps & overlaid contours
```{r comp contour 15 16 release, echo=FALSE, fig.height=4, fig.width=8}
  # heatmap of 2016-rel1 vs 2016-rel2
   #png("Graphics/kernelUD_heatmapgrp12.png", width=7, height=4, units="in", res=600) 
    par(mfrow=c(1,2))
     image(vud16.g1[[1]], col=c(heat.colors(6),"white"), main="LFC 2016, Group 1; h=3.03")
      contour(xyz.g1.16, add=TRUE, nlevels=6, drawlabels=FALSE)  
            plot(river3, add=T, col="grey60")
     image(vud16.g2[[1]], col=c(heat.colors(6),"white"), main="LFC 2016, Group 2; h=3.03")
      contour(xyz.g2.16, add=TRUE, nlevels=6, drawlabels=FALSE)
            plot(river3, add=T, col="grey60")
  #dev.off()   
    
  # overlaid contours 
  # png("Graphics/kernelUD_contoursgrp12.png", width=10,height=3, units="in", res=600)
   par(mfrow=c(1,3))
     contour(xyz.g1.16, add=FALSE, nlevels=5, levels=25, drawlabels=FALSE, lwd=2.5, col="red", main="25% contour")
     contour(xyz.g2.16, add=TRUE, nlevels=5, levels=25, drawlabels=FALSE, lwd=2.5, col="steelblue2")
       plot(river3, add=T, col="grey60")
     legend("topleft", legend=c("Group 1","Group 2"), fill=c("red","steelblue2"))
     contour(xyz.g1.16, add=FALSE, nlevels=5, levels=50, drawlabels=FALSE, lwd=2.5,col="red", main="50% contour")
     contour(xyz.g2.16, add=TRUE, nlevels=5, levels=50, drawlabels=FALSE, lwd=2.5,col="steelblue2")
       plot(river3, add=T, col="grey60")
     contour(xyz.g1.16, add=FALSE, nlevels=5, levels=75, drawlabels=FALSE, lwd=2.5,col="red", main="75% contour")
     contour(xyz.g2.16, add=TRUE, nlevels=5, levels=75, drawlabels=FALSE, lwd=2.5,col="steelblue2")
       plot(river3, add=T, col="grey60")
  #dev.off()
```

______________________


# Extract cell values from vud / xyz objects
```{r extract grid values}
  # final kud objects: kud15, kud16, kud16.g1, kud16.g2, kud16.grid2
  # final vud objects: vud15, vud16, vud16.g1, vud16.g2, vud16.grid2
  # final xyz volume objects: xyz.15, xyz.16, xyz.g1.16, xyz.g2.16, xyz.grid2
  
  r15 = raster(xyz.15)
  r16 = raster(xyz.16)
  r16g1 = raster(xyz.g1.16)
  r16g2 = raster(xyz.g2.16)
  # r16grid2 = raster(xyz.grid2)
  
  grid15.kud = data.frame(cbind(kud15$LFC@coords, kud15$LFC@data$ud))
    names(grid15.kud) <- c("Easting","Northing","UD")
  grid15.vud = data.frame(cbind(vud15$LFC@coords, vud15$LFC@data$n))
    names(grid15.vud) <- c("Easting","Northing","volUD")
   grid15.ud = merge(grid15.kud, grid15.vud)

  grid16.kud = data.frame(cbind(kud16$LFC@coords, kud16$LFC@data$ud))
    names(grid16.kud) <- c("Easting","Northing","UD")
  grid16.vud = data.frame(cbind(vud16$LFC@coords, vud16$LFC@data$n))
    names(grid16.vud) <- c("Easting","Northing","volUD")
   grid16.ud = merge(grid16.kud, grid16.vud)

  grid16.g1.kud = data.frame(cbind(kud16.g1$LFC@coords, kud16.g1$LFC@data$ud))
    names(grid16.g1.kud) <- c("Easting","Northing","UD")
  grid16.g1.vud = data.frame(cbind(vud16.g1$LFC@coords, vud16.g1$LFC@data$n))
    names(grid16.g1.vud) <- c("Easting","Northing","volUD")
   grid16.g1.ud = merge(grid16.g1.kud, grid16.g1.vud)

  grid16.g2.kud = data.frame(cbind(kud16.g2$LFC@coords, kud16.g2$LFC@data$ud))
    names(grid16.g2.kud) <- c("Easting","Northing","UD")
  grid16.g2.vud = data.frame(cbind(vud16.g2$LFC@coords, vud16.g2$LFC@data$n))
    names(grid16.g2.vud) <- c("Easting","Northing","volUD")
   grid16.g2.ud = merge(grid16.g2.kud, grid16.g2.vud)
```

# convert points to raster to plot cleaning and match up with aarons
```{r aaron plot}
#    # plot as simple heat map to match aarons better (no contours)
#    ggplot(data = grid16.g1.ud, aes(x=Easting, y=Northing, color=UD)) + geom_point() +
#       #scale_colour_gradientn(colours=c("red","orange","yellow","lightgreen", "cyan","darkblue","white"),             
#       scale_colour_gradientn(colours=c("white","darkblue","cyan", "lightgreen","yellow","orange","red"),
#                        guide="colorbar")
   
   # make it spatial
   library(sp)
   library(rgdal)
   coordinates(grid16.g1.ud) = ~Easting+Northing

   # assign proper projection
    proj4string(grid16.g1.ud) <- map.proj # set it to lat-long
    #grid16.g1.ud = spTransform(grid16.g1.ud,CRS("insert your proj4 string here"))

    # tell R this is gridded
    gridded(grid16.g1.ud) = TRUE

    # use the raster package to convert to a raster and set its CRS:
    r16g1ud = raster(grid16.g1.ud[,1])
     projection(r16g1ud) = map.proj
   r16g1vud = raster(grid16.g1.ud[,2])
     projection(r16g1vud) = map.proj

    # Now have a look:
     colorramp.ud = c("white","darkblue","dodgerblue","aquamarine", "lightgreen","yellow","gold","orange","red","darkred")   
      plot(r16g1ud, col=colorramp.ud, interpolate=TRUE, asp=1, main="First Release (UD)")
     colorramp.vud = c("red","orange","gold","yellow","lightgreen","aquamarine","steelblue1", "dodgerblue","darkblue","white")
      plot(r16g1vud, col=colorramp.vud, interpolate=TRUE, asp=1, main="First Release (VUD)")
      plot(river3, add=TRUE)
     
      
    #### get bathymetry file from aaron and underlay it here  
      
      
# ### help code that might make grid size smaller
# #defining spatial grid data frame
# S=5 #scale to which it is to be converted
# psize<-psdeg[1]/S    # psdeg is the pixel size of old grid
# bb<-c@bbox #bounding box where "c" is the old grid
# 
# cs <- c(psize, psize) #new cell size
# cc <- bb[, 1] + (cs/2) # new cell centre
# cd <- ceiling(diff(t(bb))/cs) # new cell dimensions
# 
# deggrid <- GridTopology(cellcentre.offset=cc,cellsize=cs,cells.dim=cd) # grid formation
# 
# k<-array(0,c(Mdeg*Ndeg*S^2)) #dataframe for new grid
# 
# class<-array(k)
# class<-as.data.frame(class) 
# Ddeg <- SpatialGridDataFrame(deggrid, class , proj4string = "+proj=utm +zone=35 +south +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs") # spatial grid dataframe formation
```

## Subtract rasters to discribe and plot differences
```{r}
    # make it spatial
    coordinates(grid16.g2.ud) = ~Easting+Northing

    # assign proper projection
    proj4string(grid16.g2.ud) <- map.proj # set it to lat-long
    #grid16.g1.ud = spTransform(grid16.g1.ud,CRS("insert your proj4 string here"))

    # tell R this is gridded
    gridded(grid16.g2.ud) = TRUE

    # use the raster package to convert to a raster and set its CRS:
    r16g2 = raster(grid16.g2.ud)
     projection(r16g2) = map.proj

     # subtract g1 and g2
     trash = r16g2 - r16g2
 
     plot(trash)
```

## Look at centroid of highest density   
```{r}   
  # pull the centroid of the grid cell with the maximum density for each group 
   max15 = grid15.ud[which(grid15.ud$UD == max(grid15.ud$UD)),]
   max16 = grid16.ud[which(grid16.ud$UD == max(grid16.ud$UD)),]
   max16.g1 = grid16.g1.ud[which(grid16.g1.ud$UD == max(grid16.g1.ud$UD)),]
   max16.g2 = grid16.g2.ud[which(grid16.g2.ud$UD == max(grid16.g2.ud$UD)),]
#  max.grid2 = grid16.grid2.ud[which(grid16.grid2.ud$UD == max(grid16.grid2.ud$UD)),]
    
  # look at these on the graphic
  windows(); par(mfrow=c(2,2))
  image(xyz.15, main="2015 all", asp=1)  
   abline(h=max15$Northing, col="blue")
   abline(v=max15$Easting, col="blue")
   text(max15$Easting+30, max15$Northing-30, paste(round(max15$Easting,0),round(max15$Northing,0),sep=", "), adj=0, cex=.8)
  image(xyz.16, main="2016 all", asp=1)  
   abline(h=max16$Northing, col="blue")
   abline(v=max16$Easting, col="blue")
   text(max16$Easting+30, max16$Northing-30, paste(max16$Easting,max16$Northing,sep=", "), adj=0, cex=.8)
  image(xyz.g1.16, main="2016 Group 1", asp=1)  
   abline(h=max16.g1$Northing, col="blue")
   abline(v=max16.g1$Easting, col="blue")
   text(max16.g1$Easting+30, max16.g1$Northing-30, paste(max16.g1$Easting,max16.g1$Northing,sep=", "), adj=0, cex=.8)
  image(xyz.g2.16, main="2016 Group 2", asp=1)  
   abline(h=max16.g2$Northing, col="blue")
   abline(v=max16.g2$Easting, col="blue")
   text(max16.g2$Easting+30, max16.g2$Northing-30, paste(max16.g2$Easting,max16.g2$Northing,sep=", "), adj=0, cex=.8)
   
   
  # look at these on the graphic - comparing grid of 10 and a grid of 2
  windows(); par(mfrow=c(1,2))
  image(xyz.16, main="Grid Cells 10x10 - 2016 all", asp=1)  
   abline(h=max16$Northing, col="blue")
   abline(v=max16$Easting, col="blue")
   text(max16$Easting+30, max16$Northing-30, paste(max16$Easting,max16$Northing,sep=", "), adj=0, cex=.8)
  image(xyz.grid2, main="Grid Cells 2x2 - 2016 all", asp=1)  
   abline(h=max.grid2$Northing, col="blue")
   abline(v=max.grid2$Easting, col="blue")
   text(max.grid2$Easting+30, max.grid2$Northing-30, paste(max.grid2$Easting,max.grid2$Northing,sep=", "), adj=0, cex=.8)
   
```  