---
title: "Exploration for Data Filtering HPE"
author: "Anna Steel"
date: "August 10, 2016"
output: pdf_document
---

```{r, include=FALSE} 
# required packages
library(dplyr)
library(sp)
library(rgdal)
library(rgeos)
library(ggplot2)
library(grid) 
library(cowplot)
library(viridis)
library(maptools)
```

### Read in Data 
- Open script from Fremont16.Rproj in GitHub to ensure directories are correct
``` {r, echo=FALSE}
 load("Maestros/alldf.RData") # object 'alldf'
 options("digits.secs"=6)
 alldf$Time <- as.POSIXct(as.character(alldf$Time), format="%Y-%m-%d %H:%M:%OS", tz = "GMT")

 # N fish & positions beginning in dataframe
 print(paste0("Prior to filtering, ",nrow(alldf)," total positions in dataset"))
 print(paste0("Prior to filtering, ",length(unique(alldf$Id))," inidividual fish positioned"))
```

### Initial Data Cleaning
- remove exessively high HPEs (<1000) for ease later
- reduce dataset to only postions recorded after full VPS array was in place (don't yet have removal dates, so not incorporated here)
- Create points in a spatial dataframe as well (both lat-long WGS84 & UTM)
- other steps to include here?
-- perhaps the tags with ID > 65000 are not fish tags for our study; the VEMCO report only considered those with tagIDs in the 36xxx, 38xxx, and 39xxx series; when we remove the 5 tags in the 65xxx series our initial values for n fish tags and n positions match those in the vemco report

``` {r, echo=FALSE}
 # remove fish tags in the 65xxx series (5 tags)
 alldf <- alldf[alldf$Id<65000,]  # matches VEMCO 
 
 # excessive HPEs (>1000)
 alldf <- alldf[alldf$Hpes<1000,]  # removes 5 detections
  print(paste0("Removing ",nrow(alldf[alldf$Hpes>=1000,])," positions with HPEs > 1000"))
 
 # incomplete array
 alldfg <- alldf[alldf$Time > as.POSIXct("2016-02-109 14:00:00", tz="GMT"),]
  print(paste0(nrow(alldf) - nrow(alldfg)," positions removed due to incomplete VPS array"))
  
 # sp dataframes
alldfg.sp <- SpatialPointsDataFrame(coords = alldfg[,c("Longitude","Latitude")], 
              data = alldf, proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
        # confirmed string with VEMCO; the XY coords in azimuthal equal area
alldfg.utm <- spTransform(alldfg.sp, CRS("+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"))

```

***


### Explore HPEs relationship with measured error for sync and reference tags 
- Only positions with Hpes<1000
- Uses XY coordinates from VEMCO (Azimuthal Equal Area Projection)

``` {r, echo=FALSE, warning=FALSE}
   allsync <- read.csv("C:/Users/Anna/Documents/03_SacBankUSACE/FremontWeir2016/DATA/Positions/AllSyncRef.csv")

   options("digits"=15)
   calibsync <- read.csv("C:/Users/Anna/Documents/03_SacBankUSACE/FremontWeir2016/DATA/AnalysisPack1/CalibratedStationPositions.csv")
   calib.nameindex = read.csv("C:/Users/Anna/Documents/03_SacBankUSACE/FremontWeir2016/DATA/AnalysisPack1/CalibratedStationPositionsIndex.csv")
   calibsync <- merge(calib.nameindex, calibsync, by="Name", all.x=T)
    names(calibsync) <- c("Name","Id","LongId","TrueLat","TrueLon","TrueX","TrueY")
  
   allsync.calib <- merge(allsync, calibsync[,c("Id","TrueLat","TrueLon", "TrueX","TrueY")], by="Id", all.x=T) 
    allsync.calib <- allsync.calib[allsync.calib$Hpes<1000,]
    allsync.calib$Time = as.POSIXct(allsync.calib$Time, tz="GMT")

  # Calculate distance btwn lat-long coords
   allsync.calib$error_m =  sqrt((allsync.calib$TrueX - allsync.calib$X)^2 + (allsync.calib$TrueY - allsync.calib$Y)^2)
  
 # point data for measured error vs HPEs - removed b/c time consuming and not informative
#   plot(allsync.calib$error_m ~ allsync.calib$Hpes, xlim=c(0,1000), ylab="measured error", xlab="HPEs")
   
  # calculate average errors for binned data
    median(allsync.calib$error_m[allsync.calib$Time < as.POSIXct("2016-03-09", tz="GMT")])
    
    hpetable = dplyr::select(allsync.calib, error_m, Hpes)
    hpetable = hpetable[hpetable$Hpes<=50,]     # subset b/c 99.9% of all positions have HPEs<43

   binsize=0.25
    breaks = binsize*(c(0:(50/binsize)))[1:200]
    hpetable$group = findInterval(hpetable$Hpes,breaks)

   binstats = hpetable %>%
     group_by(group) %>%
     summarize( meanHPEm=mean(error_m), 
                medianHPEm=median(error_m),
                quant90HPEm=quantile(error_m, 0.9),
                quant95HPEm=quantile(error_m, 0.95))%>%
     mutate(bincent = (binsize*group)-(binsize/2)) %>%
     data.frame()

  # plot bin moments
   viridiscol = viridis(4)
    hpestats = ggplot(binstats, aes(x=bincent, y=quant95HPEm)) + #95%
         geom_point(aes(x=bincent, y=meanHPEm), colour=viridiscol[1]) + 
         geom_point(aes(x=bincent, y=medianHPEm), colour=viridiscol[2]) + 
         geom_point(aes(x=bincent, y=quant90HPEm), colour=viridiscol[3]) + 
         #geom_point(aes(x=bincent, y=quant95HPEm), colour=viridiscol[4]) + 
         geom_smooth(aes(x=bincent, y=meanHPEm), colour=viridiscol[1], se=FALSE) + 
         geom_smooth(aes(x=bincent, y=medianHPEm), colour=viridiscol[2], se=FALSE) + 
         geom_smooth(aes(x=bincent, y=quant90HPEm), colour=viridiscol[3], se=FALSE) + 
         #geom_smooth(aes(x=bincent, y=quant95HPEm), colour=viridiscol[4], se=FALSE) + 
         geom_hline(yintercept = 5, lty=2) + geom_hline(yintercept = 10, lty=3) +
         annotate("text",x=0, y=90, label="Sync and Reference\nTag Positions", size=5,adj=0) + 
         annotate("text",x=-0.25, y=7.5, label="Error = 5m", colour="gray70", size=3,adj=0) + 
         annotate("text",x=-0.25, y=12, label="Error = 10m", colour="grey70", size=3, adj=0) + 
         annotate("text",x=1, y=0, label="mean", colour=viridiscol[1]) + 
         annotate("text",x=3, y=0, label="median", colour=viridiscol[2]) + 
         annotate("text",x=5, y=0, label="90%ile", colour=viridiscol[3]) + 
         #annotate("text", x=7, y=0, label="95%ile",colour=viridiscol[4]) +
        theme_bw() + ylab("Measured Error") + xlab("Calculated HPEs") + xlim(-0.5,8) + ylim(0,100)
    
    # create a table to plot the % of data at each threshold of HPEs  (time consuming step)
    cumperc = data.frame(HPEs = seq(0,50, by=.25), CumPos = NA, PercPos=NA)
    for(i in 1:nrow(cumperc)) {cumperc[i,2] <- nrow(allsync[allsync$Hpes<cumperc[i,1],])}
    cumperc$PercPos = cumperc$CumPos / nrow(allsync)
    
    hpeperc = ggplot(cumperc, aes(x=HPEs-.25/2, y=PercPos, width = .225)) + geom_bar(stat="identity", fill="grey80") + theme_bw() + xlim(-0.5, 8) + xlab("Calculated HPEs") + ylab("% of Positions Retained")
    
    png("Graphics/HPE_MeasVsCalib.png", width=5, height=6, units="in", res=600)
    ggdraw() + draw_plot(hpestats, 0.05,.3,0.95,.7) + draw_plot(hpeperc, 0.05, 0, 0.95, .275) +
      draw_plot_label(c("A","B"),c(0,0), c(.95,.20), size=12)
    dev.off()
    
    print(paste0("At threshold of HPEs<0.5, mean measured error (m) of sync/ref positions = ",round(mean(allsync.calib$error_m[allsync.calib$HPEs<0.5]),2)))
    print(paste0("At threshold of HPEs<0.5, median measured error (m) of sync/ref positions = ",round(median(allsync.calib$error_m[allsync.calib$HPEs<0.5]),2)))
    print(paste0("At threshold of HPEs<0.5, 90%ile of measured error (m) of sync/ref positions = ",round(quantile(allsync.calib$error_m[allsync.calib$HPEs<0.5],0.9),2)))
    print(paste0("At threshold of HPEs<0.5, ", round(nrow(allsync.calib[allsync.calib$HPEs<0.5,])/nrow(allsync.calib)*100,2), "% of sync/ref positions retained"))     
```    
Based on these graphics I will use a HPE filtering threshold of HPE=0.5
- In the Fremont 2015 report we used an HPE of 0.5: this retained 52.8% of the positions, with a median of 144 detections per fish. Vemco estimated that this threshold (in 2015) resulted in 50% fish positions had error less than 1.21m, while 95% of positions had error <4.17m (90%ile was 2.84m).
- The vemco reports for 2016 release 1&2, at HPE<0.5, show 68% of fish positions were retained, and 50% had errors < 1.57m while 95% had errors < 4.62. This is more comparable to 2015 HPE<0.5 (50% = 1.68, 95% = 5.86). 
***


### Spatial distribution of HPEs in fish positions (Similiar to Fig 9 in 2015 report)
- Eventually will add river line to these plots but needs more research to do in ggplot
``` {r, echo=FALSE, warnings=FALSE, fig.height=9}
  nHighHpe <- nrow(alldfg[alldfg$Hpes>=5,])
  nLowHpe <- nrow(alldfg[alldfg$Hpes<5 & alldfg$Hpes>=0.5,])
  nKeepHpe <- nrow(alldfg[alldfg$Hpes<0.5,])
  
  percHigh <-(nHighHpe/(nLowHpe+nHighHpe+nKeepHpe))*100
  percLow <-(nLowHpe/(nLowHpe+nHighHpe+nKeepHpe))*100
  percKeep <- (nKeepHpe/(nLowHpe+nHighHpe+nKeepHpe))*100
    
  # read in the river channel and project properly
  riverbank = readOGR(dsn="GIS/2004_channel", layer="2004_channel_freTightclipWGS84")
     # convert to be useful in ggplot; still not sure what this actually does       
      ggriverbank <- fortify(riverbank, region="BYDEL")
      
    highhpe=ggplot(data=alldfg[alldfg$Hpes>=5 & alldfg$Hpes<50,], aes(y=Latitude, x=Longitude)) + 
      geom_point(aes(colour=Hpes), size=1.5) + 
      geom_path(data = ggriverbank, aes(long, lat, group=group)) +
      scale_colour_gradient2(name="HPEs", low = "green3", mid="yellow", high = "red", midpoint=15, space = "rgb", na.value = "grey50", guide = "colourbar") +
      ggtitle(paste0("Positional HPEs > 5: ",round(percHigh,1),"% of all positions")) +
      scale_y_continuous(breaks=seq(38.758,38.764,0.001)) + 
      scale_x_continuous(breaks=seq(-121.672, -121.664, 0.001)) +
      coord_fixed() + 
      theme_bw() + theme(title=element_text(vjust=2), axis.title.x=element_text(vjust=-.5),axis.title.y=element_text(vjust=1))

    lowhpe = ggplot(alldfg[alldfg$Hpes<5 & alldfg$Hpes>=0.5,], aes(y=Latitude, x=Longitude)) + 
      geom_point(aes(colour=Hpes), size=1.5) + 
      geom_path(data = ggriverbank, aes(long, lat, group=group)) +
      scale_colour_gradient2(name="HPEs", low = "green3", mid="yellow", high = "red", midpoint=3, space = "rgb", na.value = "grey50", guide = "colourbar") +
      ggtitle(paste0("Positional HPEs from 1 to 5: ",round(percLow,1),"% of all positions")) +
      scale_y_continuous(breaks=seq(38.758,38.764,0.001)) + 
      scale_x_continuous(breaks=seq(-121.672, -121.664, 0.001)) +
      coord_fixed() + 
      theme_bw() + theme(title=element_text(vjust=2), axis.title.x=element_text(vjust=-.5),axis.title.y=element_text(vjust=1))
    
    keephpe = ggplot(alldfg[alldfg$Hpes<0.5,], aes(y=Latitude, x=Longitude)) +
      geom_point(aes(colour=Hpes), size=1.5) + 
      geom_path(data = ggriverbank, aes(long, lat, group=group)) +
      scale_colour_gradient2(name="HPEs", low = "green3", mid="yellow", high = "red", midpoint=.8, space = "rgb", na.value = "grey50", guide = "colourbar") +
      ggtitle(paste0("Positional HPEs < 1: ",round(percKeep,1),"% of all positions")) +
      scale_y_continuous(breaks=seq(38.758,38.764,0.001)) + 
      scale_x_continuous(breaks=seq(-121.672, -121.664, 0.001)) +
      coord_fixed() + 
      theme_bw() + theme(title=element_text(vjust=2), axis.title.x=element_text(vjust=-.5),axis.title.y=element_text(vjust=1))
    
     plot_grid(highhpe, lowhpe, keephpe, nrow=3, ncol=1)

```


# code pulled from 2015 to plot density contours of removed positions (based on HPE>0.5)
```{r density plots fig 9}

   ggplot(ggriverbank) +  aes(long,lat,group=group, fill = id) +
          geom_path(color="black") +
          coord_equal() + theme_bw()

    # create the constant theme and plots      
    roundfunc <- function(l) { (l <- round(l, 3))}  
     commonTheme = list(labs(color="Density",fill="Density",
                x="Longitude", y="Latitude"),
           theme_bw(),
           theme(legend.position=c(0,1),
                 legend.justification=c(0,1)))
       
     
      ptdens.keep =  ggplot(data=alldf[alldf$Hpes<0.5,], 
                              aes(x=Longitude,y=Latitude)) + 
            geom_point(alpha=.1, color="grey80") + 
            stat_density2d(aes(fill=..level..,alpha=..level..), 
                           geom='polygon',colour='black') + 
            scale_fill_continuous(low="white",high="blue") +
            guides(alpha="none") + coord_fixed(ratio=1) + 
            geom_path(data = ggriverbank, aes(long, lat, group=group)) +
            scale_y_continuous(label=roundfunc) +  
            scale_x_continuous(label=roundfunc) + 
            commonTheme

        ptdens.remove =  ggplot(data=alldf[alldf$Hpes>=0.5 & alldf$Hpes<500,], 
                                aes(Longitude,Latitude)) + 
            geom_point(alpha=.1, color="grey80") + 
            stat_density2d(aes(fill=..level..,alpha=..level..), 
                           geom='polygon',colour='black') + 
            scale_fill_continuous(low="white",high="red") +
            guides(alpha="none") + coord_fixed(ratio=1) + 
            geom_path(data = ggriverbank, aes(long, lat, group=group)) +
          scale_y_continuous(label=roundfunc,
                             limits=range(ggriverbank$lat)) +  
            scale_x_continuous(label=roundfunc, 
                               limits=range(ggriverbank$long)) +
            commonTheme
        
        # print plots in proper grid

    png("Graphics/Figure9_HPE_Spatial_Distn.png", width=5, height=9, units="in", res=600)
      plot_grid(ptdens.remove, ptdens.keep, labels = c("A", "B"), ncol=1, align="v")
    dev.off()
    
    
```

###  Implement HPEs threshold in filtering
- This DOES NOT match the report from VEMCO (they report 106,529 or 87% after filtering to HPE<1)
- I need to get the tagID metadata from someone; suspect there are tags here that aren't fish tags
```{r, echo=FALSE, warnings=FALSE}  
  reddf = alldfg[alldfg$Hpes < 0.5,]
   print("After filtering @ HPEs<0.5, dataset retained:")
   print(paste0("  ",nrow(reddf)," positions,")) # 106529
   print(paste0("  ",round(nrow(reddf)/nrow(alldfg)*100,2), "% of fish tag positions"))  # 86.63%
   print(paste0("  ",length(unique(reddf$Id))," individual fish"))  # 433
   
  reddf.sp <- SpatialPointsDataFrame(coords = reddf[,c("Longitude","Latitude")], data = reddf, proj4string=CRS("+proj=aeqd +lat_0=38.759985 +lon_0=-121.666908 +x_0=1000 +y_0=1000 +datum=WGS84"))
   # proj4string directly from VEMCO documentation
  
  dropdf = alldfg[alldfg$Hpes >=0.5,]
  dropdf.sp <- SpatialPointsDataFrame(coords = dropdf[,c("Longitude","Latitude")], data = dropdf, proj4string=CRS("+proj=aeqd +lat_0=38.759985 +lon_0=-121.666908 +x_0=1000 +y_0=1000 +datum=WGS84"))
   # proj4string directly from VEMCO documentation
 
```

Here is an excerpt from VEMCO's results document that is returned with the post-processed VPS dataset, regarding thier estimate of the precision of the fish positions:

> Fish tag precision is estimated here using a simple method of comparing pairs of calculated positions
> that are very close in time, based on the knowledge that over a short period of time a fish will travel a
> relatively short distance. The time durations between successive transmissions of a fish tag in this study
> follow a pseudorandom sequence, with a minimum of 1.0 seconds, a maximum of 2.0 seconds, and an
> average of 1.5 seconds.
> For each of the HPEs filters, the retained positions are analyzed as follows:
> • Pairs of positions from the same transmitter that are within 2.0 seconds of each other are
> identified, and the horizontal distances between these pairs of positions are calculated
> • Selected percentiles of these horizontal distances are calculated
> The following is a summary of these analyses:
> HPEs  # Pos  % pos  50%ile 80%ile 90%ile 95%ile
> 0.2   25792   21%   1.34    2.04    2.56   3.16
> 0.5   83658   68%   1.57    2.54    3.45   4.62
> 1.0  106529   87%   1.68    2.93    4.21   5.86
> For example, using an HPEs filter of 1.0, half of the pairs of calculated positions that are within 2.0
> seconds of each other are less than 1.68 metres apart, and 80% are within 2.93m.
> Note that these statistics cannot be compared directly with the corresponding statistics for sync and
> reference tags because they include a component based on an average of 1.5 seconds of fish motion.

***

### Histograms of individual detections/GoodBasic positions for each calculated fish location:
- not of much interest but code was already written
``` {r, echo=FALSE} 
  ### not in report ###
 par(mfrow=c(2,2))
  hist(alldfg$GoodBasicCount, breaks=25, main="All Positions:\nNumber of Good Basic positions \nper estimated position", xlab="N Good Basic Positions", xlim=c(0,25))
  hist(reddf$GoodBasicCount, breaks=25, main="Positions HPEs<0.5:\nNumber of Good Basic positions \nper estimated position", xlab="N Good Basic Positions", xlim=c(0,25))

  hist(alldfg$DetectionsCount, breaks=25, main="All Positions:\nNumber of Detections \nper estimated position", xlab="N Detections", xlim=c(0,25))
  hist(reddf$DetectionsCount, breaks=25, main="Positions HPEs<0.5:\nNumber of Detections \nper estimated position", xlab="N Detections", xlim=c(0,25))
```

### Positions remaining per fish (Figs 8 and 10 in 2015 report)
- considered positions per fish before filtering by HPE and after
+ plots tracks of outliers to examine for predator-like behavior patters
+ 'outliers' defined according to standard boxplot metrics: all those points greater than 1.5*IQR + 75%ile of the data.
- plots percent of positions remaining for individual fish after filtering at HPE<1 (Fig 8)
```{r, echo=FALSE, fig.height=8, fig.width=7}
 # prior to HPE filtering
 all.npf = alldfg %>%
   group_by(Id) %>%
   summarize(npos.all=n())%>%
   data.frame()

  summary(all.npf$npos.all)
  
  #png("Graphics/Figure8a_HPE_PosPerFish.png", width=6, height=5, units="in", res=600)
   hist(all.npf$npos.all, xlim=c(0,1000), breaks=250, ylim=c(0,110),
        xlab=c("Number of Positions"), main="Positions recorded per fish\nprior to HPE filtering")  
    text(x=800, y=40, "Removed two individual tags\nw/ > 5000 detections", font=3)
  #dev.off()
  
  hist(all.npf$npos.all, xlim=c(0,1000), breaks=250, ylim=c(0,110),
        xlab=c("Number of Positions"), main="Positions recorded per fish\nprior to HPE filtering")  
    text(x=800, y=40, "Removed two individual tags\nw/ > 5000 detections", font=3)
  
    
  outliers.pre = all.npf[all.npf$npos.all %in% sort(boxplot.stats(all.npf$npos.all)$out),]
      
  ggplot(data=alldfg[alldfg$Id %in% outliers.pre$Id,], aes(x=Longitude, y=Latitude)) + geom_point() +
    facet_wrap(~Id, ncol=4) + ggtitle("Tracks of outliers, positions not filtered")

 # after HPE filtering
 red.npf = reddf %>%
   group_by(Id) %>%
   summarize(npos.red= n()) %>%
   data.frame()
     
  summary(red.npf$npos.red)   
  
  #png("Graphics/Figure8b_HPE_PosPerFish.png", width=6, height=5, units="in", res=600)
    hist(red.npf$npos.red, xlim=c(0,1000), breaks=100, ylim=c(0,110), 
         xlab=c("Number of Positions"), main="Positions recorded per fish\nafter HPE filtering")  
     text(x=800, y=40, "Removed two individual tags\nw/ > 2000 detections", font=3)
  #dev.off()
  
  outliers.post = red.npf[red.npf$npos.red %in% sort(boxplot.stats(red.npf$npos.red)$out),]
        
  ggplot(data=reddf[reddf$Id %in% outliers.post$Id,], aes(x=Longitude, y=Latitude)) + geom_point() +
              facet_wrap(~Id, ncol=4) + ggtitle("Tracks for outliers, positions filtered HPEs<0.5")
```

```{r, echo=FALSE, warnings=FALSE}
  # percent of positions remaining per individual fish (Fig 10)
  
 comp.npf = merge(all.npf, red.npf, by="Id")
 comp.npf$perc.remain = comp.npf$npos.red / comp.npf$npos.all
 
 filtlevel = ggplot(data = alldfg, aes(Hpes)) + 
    geom_histogram(binwidth=.2, col=I("black"), fill="grey95") + 
    ggtitle("Calculated HPEs, all positions") + 
    scale_x_continuous(breaks=seq(0,10,2), limits=c(0,10)) + 
    xlab("HPEs") + ylab("Frequency") + 
    theme_bw() + 
    theme(title=element_text(vjust=2), 
          axis.title.x=element_text(vjust=-.5),
          axis.title.y=element_text(vjust=1.2),
          plot.margin=unit(c(1,1,1.25,1), "cm")) +
    geom_vline(xintercept = 0.5, col="red", lty=2) + 
    annotate("text",x=1.1, y=50100, label="HPEs = 0.5", col="red", adj=0, size=4)

 filt.ppf = ggplot(data = comp.npf, aes(npos.red)) + 
    geom_histogram(binwidth=25, col=I("black"), fill="grey95") + 
    ggtitle("Filtered at HPEs<0.5:
            
Positions per Fish") +  
    scale_x_continuous(breaks=seq(0,500,100), limits=c(0,500)) + 
    scale_y_continuous(breaks=seq(0,70,20), limits=c(0,70)) + 
    xlab("N Positions") + ylab("Frequency") + 
    theme_bw() + 
    theme(title=element_text(vjust=2), 
          axis.title.x=element_text(vjust=-.5),
          axis.title.y=element_text(vjust=1.2),
          plot.margin=unit(c(.1,1,.75,.5), "cm"))

 filt.proprem = ggplot(data = comp.npf, aes(perc.remain)) + 
    geom_histogram(binwidth=.025, col=I("black"), fill="grey95") + 
    ggtitle("Proportion Positions\nRemaining per Fish") + 
    scale_x_continuous(breaks=seq(0,1,.2), limits=c(0,1)) + 
    scale_y_continuous(breaks=seq(0,85,20), limits=c(0,85)) + 
    xlab("Proportion") + ylab("Frequency") + 
    theme_bw() + 
    theme(title=element_text(vjust=2), 
          axis.title.x=element_text(vjust=-.5),
          axis.title.y=element_text(vjust=1.2),
          plot.margin=unit(c(.1,1,.75,.5), "cm"))

        
       png("Graphics/Figure10_Filtered_ComboFigure.png", width=8, height=4.75, units="in", res=300)
        ggdraw() + 
          draw_plot(filtlevel, x=0,y=0,width=.6, height=1) + 
          draw_plot(filt.ppf, x=.6,y=.475,width=.4, height=0.45) + 
          draw_plot(filt.proprem, x=.6,y=0.025,width=.4, height=0.45) +  
          draw_plot_label(label=c("A","B","C"), x=c(0.05,0.62,0.62), y=c(.975,.88,.45), size=16)
        dev.off()
```
 
### Look at fish which >40% positions removed
- how many are there?
- are the tracks indicative of predator behavior?
- where are the errors?
```{r, echo=FALSE, warnings=FALSE}
  # how many?      
   poorHpes = comp.npf[comp.npf$perc.remain<=.6,]  # 2 fish
      print(paste0("Only ",nrow(poorHpes)," fish with >40% of positions removed"))
   poor.dfg = alldfg[alldfg$Id %in% poorHpes$Id,]

  # where are the errors in the 'bad' tracks?
  ggplot(data=poor.dfg[order(poor.dfg$Hpes),], aes(x=Longitude, y=Latitude, color=(Hpes))) + 
    geom_point() + coord_fixed() + 
    facet_wrap(~Id, ncol=4) + 
    scale_colour_gradientn(colours=rev(viridis(5)))
  
  # does the track change significantly when the poor Hpes points are removed? No
  poor.pre = ggplot(data=alldfg[alldfg$Id %in% poorHpes$Id,], aes(x=Longitude, y=Latitude)) + geom_point() + 
    facet_wrap(~Id, ncol=4) + ggtitle("'Poor' tracks with no filtering")
  poor.post = ggplot(data=alldfg[alldfg$Id %in% poorHpes$Id & alldfg$HPEs<0.5,], aes(x=Longitude, y=Latitude)) + geom_point() + facet_wrap(~Id, ncol=4) + ggtitle("'Poor' tracks filtered at HPEs < 1")

  plot_grid(  poor.pre, poor.post, ncol=1, nrow=2)
```  


