---
title: "Data Filtering Process, Condensed"
author: "Anna Steel"
date: "August 12, 2016"
output: pdf_document
---

## Filtering of VEMCO post-processed VPS positions

This code runs from the datafiles provided by VEMCO, and builds final datasets for analysis
Also includes reference numbers to track how filtering affects the dataset

__metrics considered include number of positions, number of fish in dataset, and positions per fish__

* filters by HPE: see 'Exploration_DataFiltering' for details
* filters by speed:
* filters for likely predators:
* filters out sparse tracks:
* breaks apart tracks with large gaps (for subsequent smoothing/rediscretization)
* Remember: times are reported in UTC from vemco

```{r, include=FALSE} 
# required packages
library(dplyr)
library(sp)
library(rgdal)
library(rgeos)
library(ggplot2)
library(grid) 
library(cowplot)
library(viridis)
library(adehabitatLT)
```

### Read in Data & Clean for proper dates and TagIDs
- Open script from Fremont16.Rproj in GitHub to ensure directories are correct
- add UTM coordinates
- filter out tags in the 65xxx series
- filter any tags detected outside of period of complete array (none this year)
- tabulate total fish, total positions, and total positions per fish
``` {r}
 load("Maestros/alldf.RData")
 options("digits.secs"=6)
 alldf$Time <- as.POSIXct(as.character(alldf$Time), format="%Y-%m-%d %H:%M:%OS", tz = "GMT")

 # remove fish tags in the 65xxx series (5 tags)
 alldf <- alldf[alldf$Id<65000,]  # matches VEMCO 
 
 # incomplete array
 alldfg <- alldf[alldf$Time > as.POSIXct("2016-02-109 14:00:00", tz="GMT"),]
  print(paste0(nrow(alldf) - nrow(alldfg)," positions removed due to incomplete VPS array"))
 
 # convert the Lat Long into UTMs using 'sp'
  alldf.sp <- SpatialPointsDataFrame(coords = alldf[,c("Longitude","Latitude")], 
              data = alldf, 
              proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
        # confirmed string with VEMCO; the XY coords in azimuthal equal area
  options(digits=10)
  alldf.utm <- spTransform(alldf.sp, 
                          CRS("+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"))
  alldf.utm@data[,c("east","north")] <- alldf.utm@coords
  
  alldf.utm = alldf.utm@data   
  
 # N fish & total N positions
 print(paste0("Prior to filtering, ",nrow(alldf)," total positions in dataset"))
 print(paste0("Prior to filtering, ",length(unique(alldf$Id))," individual fish positioned"))

 # N pos per fish 
  all.npf = alldfg %>%
   group_by(Id) %>%
   summarize(npos.all=n())%>%
   data.frame()

  print("Summary of N positions per fish, after reducing to applicable data")
  summary(all.npf$npos.all)
```

### Primary HPE filter: <1.0 HPEs
After filtering @ HPEs < 1, dataset retained:
```{r}
 reddf = alldfg[alldfg$Hpes < 1,]
  
  # N fish & total N positions
   print(paste0(nrow(reddf)," positions")) # 110,211  
    print(paste0("   ",round(nrow(reddf)/nrow(alldfg)*100,2), "% of fish tag positions"))  # 84.35%
   print(paste0(length(unique(reddf$Id))," individual fish"))  # 438
    print(paste0("   ",round((length(unique(reddf$Id))/length(unique(alldf$Id)))*100,1),"% of individual fish retained "))  # 438
   
   
  # N pos per fish after HPE filtering
  red.npf = reddf %>%
   group_by(Id) %>%
   summarize(npos.red= n()) %>%
   data.frame()
  
  print("Summary of N positions per fish, after filtering at HPE<1")
  summary(red.npf$npos.red)   

```

#### Write out HPE filtered dataset
```{r}
  save(reddf, file="Maestros/AllFishPrimaryFilt.RData")
```
## End of Primary Filtering Process

***

## Beginning of Secondary Filtering Process

### Excessive Speeds Filtering
```{r}
  load("Maestros/AllFishPrimaryFilt.RData") # object called 'reddf'

  # Critical to order this properly for the ordered step analysis below (TypeI)
  reddf = reddf[order(reddf$Id, reddf$Time),]  
  reddf$IDcol = 1:nrow(reddf)

  # convert the Lat Long into UTMs using 'sp'
  reddf.sp <- SpatialPointsDataFrame(coords = reddf[,c("Longitude","Latitude")], 
              data = reddf, 
              proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
        # confirmed string with VEMCO; the XY coords in azimuthal equal area
  options(digits=10)
  reddf.utm <- spTransform(reddf.sp, 
                          CRS("+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"))
  reddf.utm@data[,c("east","north")] <- reddf.utm@coords
 
  reddf2 = reddf.utm@data    
 
  # calculate speed and distance with adehabitatLT
  red.ltraj = as.ltraj(xy=reddf2[,c("east","north")], date=reddf2$Time, 
                        id=reddf2$Id, infolocs = reddf2[,c("Id","Hpes","east","north")])
 
  red2 = ld(red.ltraj)
  red2$spd_mps = red2$dist / red2$dt
 
  # identify 'bad' positions (99%ile of step-speeds is ~7.7mps
  red2$prevspd = lag(red2$dist)/lag(red2$dt)

  red2$badpos <- 0
   red2$badpos[red2$spd_mps>7.7 & red2$prevspd>7.7] <- 1

  # filter out bad positions    
  red3 = red2[red2$badpos==0,]
 
  # recalculate speed and distance
  red3.ltraj = as.ltraj(xy=red3[,c("east","north")], date=red3$date, 
                        id=red3$Id, infolocs = red3[,c("Id","Hpes","east","north")])
 
  red4 = ld(red3.ltraj)
  red4$spd_mps = red4$dist / red4$dt
  
  save(red4, file="Maestros/AllFish_FiltSec1Speed.RData")
```
 

### Departed from and returned again to array
- Remove select bursts for fish returning to array after some time absent
```{r}  
dt_threshold = 6*3600  # 6 hours

dtcut = function(dt) { return (dt > dt_threshold) } 

red4.ltraj = dl(red4)
red5.ltraj <- cutltraj(red4.ltraj, "dtcut(dt)", nextr=TRUE)

red5 = ld(red5.ltraj)

red5 = red5[!(red5$burst %in% c(36472.3, 36472.4, 36612.2, 36612.3)),]

save(red5, file="Maestros/AllFish_FiltSec2Pred.RData")
```

### Suspect holding behavior
__Should revisit this - these might be milling smolts, but might also be a predator__
- see "Exploration_DataFilteringPreds" for more on these three tracks
```{r}
red6 = red5[!(red5$Id %in% c(36379,36483,36675)),]
save(red6, file="Maestros/AllFish_FiltSec3Hold.RData")
```

### Cut tracks into sub-bursts when gaps are > a selected threshold to avoid interpolating between them
- for now I'll use 50m until I make more time to get into this deeper. 
- see final few chunks in "Exploration_TrackGapBias" for more details on how to select this threshold.
``` {r, warnings=FALSE}
dist_threshold = 50
gapcut = function(dist) { return (dist > dist_threshold) } 

red6.ltraj = as.ltraj(xy=red6[,c("east","north")], date = red6$date, id = red6$Id, infolocs=red6[,c("Hpes","east","north")])
red7.ltraj <- cutltraj(red6.ltraj, "gapcut(dist)", nextr=TRUE)

red7 = ld(red7.ltraj)
  red7$spd_mps = red7$dist / red7$dt
  
save(red7, file="Maestros/AllFish_FiltSec4Bursts.RData")
```
 
### Plot of pre- & post-filtering positions 
```{r, echo=FALSE}
 river3 = readOGR("C:/Users/Anna/Documents/GitHub/Fremont16/GIS/2004_channel","2004_channel_freTightclip")
  f_river3 <- fortify(river3, region="BYDEL")

pre.plot <- ggplot(data = alldf.utm[alldf.utm$Hpes<50,], aes(x=east, y=north, colour=Hpes)) + geom_point(alpha=0.2) + 
  scale_color_gradientn(colors=viridis(5)) +  ggtitle("Pre-Filtering") +
  geom_path(data = river3, aes(long, lat), col="gold", size=1.2 )+
  xlim(river3@bbox[1,1]+50, river3@bbox[1,2]) + ylim(river3@bbox[2,1], river3@bbox[2,2]) +
  coord_fixed()

post.plot <- ggplot(data = red7, aes(x=east, y=north, colour=Hpes)) + geom_point(alpha=0.2) + 
  scale_color_gradientn(colors=viridis(5)) + ggtitle("Post-Filtering") +
  geom_path(data = river3, aes(long, lat), col="gold", size=1.2 )+
  xlim(river3@bbox[1,1]+50, river3@bbox[1,2]) + ylim(river3@bbox[2,1], river3@bbox[2,2]) +
  coord_fixed()

par(mar=c(5.1,4.1,4.1,3.1))
plot_grid(pre.plot, post.plot, nrow=2)

```

