---
title: "Rediscretization_Temporal - SensitivityAnalysis"
author: "Anna Steel"
date: "September 6, 2016"
output: pdf_document
---
```{r, include=FALSE} 
# required packages
library(dplyr)
library(sp)
library(rgdal)
library(rgeos)
library(maptools)
library(ggplot2)
library(grid) 
library(cowplot)
library(viridis)
library(adehabitatLT)
library(adehabitatHR)
library(stringr)
library(stringr)
library(raster)

river3 = readOGR("C:/Users/Anna/Documents/GitHub/Fremont16/GIS/2004_channel","2004_channel_freTightclip")
map.proj = CRS(river3@proj4string@projargs)

```

## Load data
```{r}
  options(digits=20) #keep 
  load("Maestros/AllFish_FiltSec5Gaps.RData")  # single object, named red9
  
   dim(red9) # 76269 detections 
   length(unique(red9$id))  # 374 unique fish
   
   ndetects.fish = summarize(group_by(red9, id), ndet = n())  
     mean(ndetects.fish$ndet) # 203.9 per fish
     range(ndetects.fish$ndet) # ranges from 22 - 578

   red9.ltraj = as.ltraj(xy=red9[,c("east","north")], date=red9$date, 
                id=factor(red9$id), burst = factor(red9$burst),
                infolocs=red9[,c("Hpes","east","north")])

```

## Set up list for collecting rediscrerized datasets
```{r}
   xx = list()
```   

## Set up dataframe for collecting step-wise SoG values after discretization (autocorrelation issues)
```{r}
  a = data.frame(interval = 2:30, meansog = NA, sdsog = NA, medsog = NA, npos = NA, nposfish = NA)
```

## Set up dataframe for collecting path-level SoG values after discretization
```{r}
  b = data.frame(interval = 2:30, mean.pspd = NA, sd.pspd = NA, med.pspd = NA, npos = NA, nposfish = NA)
```

## For this pass, I'm not going to stagger first detection
- here is the code incase I want to add it back in
```{r, echo=FALSE, eval=FALSE}
      # stagger first detection across all fish
      #   - if first detection has an x value greater than 615575 then keep it (>100m from start)
      #       - there are 64 fish for which this applies
      #   - otherwise, pick randomly from the points before that location

      # pull number of points for each id that are before the threshold
     n.prethres = red9 %>%
        filter(x<615575) %>%
        group_by(id) %>%
        summarize(n.pre = n())
     n.prethres = as.data.frame(n.prethres)
     
       # add column with the first detection selected for use for that id
       samplefunc = function(x) sample(1:x,1)
       set.seed(23)
       n.prethres$first.det = unlist(lapply(n.prethres$n.pre, samplefunc))

      # subset the original data frame using the randomly sampled first detection
     stag.prep = red9 %>%
        group_by(id) %>%
        mutate(detect.num = 1:n()) 
     stag.prep = as.data.frame(stag.prep)
     reddf.stag = merge(stag.prep, n.prethres, all.x=T)
      reddf.stag[is.na(reddf.stag$first.det),"first.det"] <- 1  # if first detection > threshold, use it
      reddf.stag = reddf.stag[order(reddf.stag$id, reddf.stag$detect.num),]
      reddf.stag = reddf.stag[reddf.stag$detect.num >= reddf.stag$first.det,]

      reddf.stag$n.pre <- NULL
      reddf.stag$detect.num <- NULL
```

## Loop including Rediscretization of Tracks & sequential point SoG calculations
- Using secondary filtered data (incl removal of positions with >150m gap) to rediscretize tracks for further analysis
- The basic stats of the resulting dataset are saved
- SoG is the speed between each position, averaged over all values (not first aggregated by fish - thus this has problems with autocorrelation)
- The mean, median, and sd of these are calculated and saved 
```{r}
  for (i in 2:30)
   { # Discretize in Time
      red9.trdz = ld(redisltraj(red9.ltraj, u=i, type="time", nnew=10))
       red9.trdz$run = "LFC" # creates a common grouping variable to make UD with all points
      red9.trdz=red9.trdz[order(red9.trdz$id,red9.trdz$date),]
   
     # recalculate migration speed  
      red9.trdz$spd_mps = red9.trdz$dist / red9.trdz$dt
       
     # save to list
      xx[[i-1]] <- red9.trdz; names(xx)[[i-1]] <- paste0("Step",i)
      
     # calculate run stats
      a[a$interval==i,"meansog"] <- round(  mean(red9.trdz$spd_mps, na.rm=T) , 3)
      a[a$interval==i,"sdsog"]   <- round(    sd(red9.trdz$spd_mps, na.rm=T) , 3)
      a[a$interval==i,"medsog"]  <- round(median(red9.trdz$spd_mps, na.rm=T) , 3)
      a[a$interval==i,"npos"]    <- round(  nrow(red9.trdz)                  , 3)

     # calculate nposfish
      ndetects.discr = summarize(group_by(red9.trdz, id), ndet = n())  
      a[a$interval==i,"nposfish"]    <- round(  mean(ndetects.discr$ndet)        , 3)
   }  
```


## Loop including Rediscretization of Tracks & Path-level SoG calculations
- Using primary and secondary filtered data (incl removal of positions with >150m gap) to rediscretize tracks for further analysis
- The basic stats of the resulting dataset are saved
- SoG is total path length / time between first and last detection, per fish
- The mean, median, and sd of these are calculated and saved 
```{r}
  for (i in 2:30)
   { # Discretize in Time
      red9.trdz = ld(redisltraj(red9.ltraj, u=i, type="time", nnew=10))
       red9.trdz$run = "LFC" # creates a common grouping variable to make UD with all points
      red9.trdz=red9.trdz[order(red9.trdz$id,red9.trdz$date),]
   
     # recalculate migration speed  
      red9.trdz$spd_mps = red9.trdz$dist / red9.trdz$dt
       
     # save to list
      xx[[i-1]] <- red9.trdz; names(xx)[[i-1]] <- paste0("Step",i)

     # calculate path-level speeds for each fish   
      options(digits=7)
      pathspd = summarize(group_by(red9.trdz,id),
                 pathlength_m = round(sum(dist, na.rm=T),1), 
                 first = min(date), last = max(date),
                 n=n())
       pathspd = data.frame(pathspd)
       pathspd$passagetime_s = as.numeric(difftime(pathspd$last, pathspd$first, units="sec"))
       pathspd$mps = pathspd$pathlength_m / pathspd$passagetime_s

      # calculate run stats
      b[b$interval==i,"mean.pspd"] <- round(  mean(pathspd$mps, na.rm=T) , 3)
      b[b$interval==i,"sd.pspd"]   <- round(    sd(pathspd$mps, na.rm=T) , 3)
      b[b$interval==i,"med.pspd"]  <- round(median(pathspd$mps, na.rm=T) , 3)
      b[b$interval==i,"npos"]    <- round(  nrow(red9.trdz)            , 3)
      b[b$interval==i,"nposfish"]<- round(  mean(pathspd$n)            , 3)
   }  
```


## Plot the Speed results
```{r}
  windows()
    plotmean = ggplot(data = b, aes(y=mean.pspd, x=interval)) +
        geom_point(col="steelblue") + geom_line(col="steelblue") + 
       xlab("Rediscretization Interval") + ylab("Mean Path\nSpeed over Ground")
    
    plotsd = ggplot(data = b, aes(y=sd.pspd, x=interval)) +
        geom_point(col="green3") + geom_line(col="green3") + 
       xlab("Rediscretization Interval") + ylab("SD of Path\nSpeed over Ground")
        
    plotmed = ggplot(data = b, aes(y=med.pspd, x=interval)) +
        geom_point(col="purple") + geom_line(col="purple") + 
       xlab("Rediscretization Interval") + ylab("Median Path\nSpeed over Ground")
    
   plot_grid(plotmean, plotsd, plotmed, ncol=1, align="v")
```

## Run saved rediscretizations through kernel density code with set smoothing parameter (h=3.03)
```{r}
  # create an even 10x10m grid for 2016
    e = extent(615430, 615430+(61*10), 4290820, 4290820+(47*10))
    r = raster(e)
    res(r) = c(10,10)   
    projection(r) = map.proj 
    grid10 = SpatialPixels(SpatialPoints(coordinates(r)))    
    
  # create an even 2x2m grid for 2016
    e = extent(615430, 615430+(610), 4290820, 4290820+(470))
    r = raster(e)
    res(r) = c(2,2)   
    projection(r) = map.proj 
    grid2 = SpatialPixels(SpatialPoints(coordinates(r)))    

  # select only 5 representative values for discretization
    xx.sel = list(Step2=xx[[2-1]], Step5=xx[[5-1]], 
                  Step10=xx[[10-1]], Step20=xx[[20-1]], 
                  Step30=xx[[30-1]])

  #  add proper projection and create kud using individually selected h, via lscv
#     projkud.lscv = function(trdz) { grp = data.frame(grp=trdz[,"run"])
#                                xytsp = (trdz[,c("x","y")])
#                                coordinates(grp) <- xytsp 
#                                proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
#                                                         +units=m +no_defs +ellps=WGS84
#                                                         +towgs84=0,0,0") 
#                                kud = kernelUD(grp[,1], h="LSCV", kern="bivnorm", 
#                                               extent=0.1, 
#                                               grid=grid10) 
#                                return(kud$LFC)}
    
  #  add proper projection and create kud using h=2
    projkud2 = function(trdz) { grp = data.frame(grp=trdz[,"run"])
                               xytsp = (trdz[,c("x","y")])
                               coordinates(grp) <- xytsp 
                               proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
                                                        +units=m +no_defs +ellps=WGS84
                                                        +towgs84=0,0,0") 
                               kud = kernelUD(grp[,1], h=2, kern="bivnorm", 
                                              extent=0.1, 
                                              grid=grid10) 
                               return(kud$LFC)}
    projkud2.g2 = function(trdz) { grp = data.frame(grp=trdz[,"run"])
                               xytsp = (trdz[,c("x","y")])
                               coordinates(grp) <- xytsp 
                               proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
                                                        +units=m +no_defs +ellps=WGS84
                                                        +towgs84=0,0,0") 
                               kud = kernelUD(grp[,1], h=2, kern="bivnorm", 
                                              extent=0.1, 
                                              grid=grid2) 
                               return(kud$LFC)}

  #  add proper projection and create kud using h=3.03
    projkud303 = function(trdz) { grp = data.frame(grp=trdz[,"run"])
                               xytsp = (trdz[,c("x","y")])
                               coordinates(grp) <- xytsp 
                               proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
                                                        +units=m +no_defs +ellps=WGS84
                                                        +towgs84=0,0,0") 
                               kud = kernelUD(grp[,1], h=3.03, kern="bivnorm", 
                                              extent=0.1, 
                                              grid=grid10) 
                               return(kud$LFC)}
   projkud303.g2 = function(trdz) { grp = data.frame(grp=trdz[,"run"])
                               xytsp = (trdz[,c("x","y")])
                               coordinates(grp) <- xytsp 
                               proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
                                                        +units=m +no_defs +ellps=WGS84
                                                        +towgs84=0,0,0") 
                               kud = kernelUD(grp[,1], h=3.03, kern="bivnorm", 
                                              extent=0.1, 
                                              grid=grid2) 
                               return(kud$LFC)}
       
   #  add proper projection and create kud using h=5
    projkud5 = function(trdz) { grp = data.frame(grp=trdz[,"run"])
                               xytsp = (trdz[,c("x","y")])
                               coordinates(grp) <- xytsp 
                               proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
                                                        +units=m +no_defs +ellps=WGS84
                                                        +towgs84=0,0,0") 
                               kud = kernelUD(grp[,1], h=5, kern="bivnorm", 
                                              extent=0.1, 
                                              grid=grid10) 
                               return(kud$LFC)}
   projkud5.g2 = function(trdz) { grp = data.frame(grp=trdz[,"run"])
                               xytsp = (trdz[,c("x","y")])
                               coordinates(grp) <- xytsp 
                               proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
                                                        +units=m +no_defs +ellps=WGS84
                                                        +towgs84=0,0,0") 
                               kud = kernelUD(grp[,1], h=5, kern="bivnorm", 
                                              extent=0.1, 
                                              grid=grid2) 
                               return(kud$LFC)}

   #  add proper projection and create kud using h=10
    projkud10 = function(trdz) { grp = data.frame(grp=trdz[,"run"])
                               xytsp = (trdz[,c("x","y")])
                               coordinates(grp) <- xytsp 
                               proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
                                                        +units=m +no_defs +ellps=WGS84
                                                        +towgs84=0,0,0") 
                               kud = kernelUD(grp[,1], h=10, kern="bivnorm", 
                                              extent=0.1, 
                                              grid=grid10) 
                               return(kud$LFC)}
    projkud10.g2 = function(trdz) { grp = data.frame(grp=trdz[,"run"])
                               xytsp = (trdz[,c("x","y")])
                               coordinates(grp) <- xytsp 
                               proj4string(grp) <- CRS("+proj=utm +zone=10 +datum=WGS84
                                                        +units=m +no_defs +ellps=WGS84
                                                        +towgs84=0,0,0") 
                               kud = kernelUD(grp[,1], h=10, kern="bivnorm", 
                                              extent=0.1, 
                                              grid=grid2) 
                               return(kud$LFC)}

     #spxx.sel = lapply(xx.sel[[1]], projkud)   # didn't work but loop does. go with it.
#     spxx.sel.lscv = list()
#     for(i in 1:5) { # can't run i=1 or i=2 b/c vector allocation is too large
#         spxx.sel.lscv[[i]] <- projkud.lscv(xx.sel[[i]])
#         names(spxx.sel.lscv)[[i]] <- names(xx.sel)[[i]]
#     }
    
    spxx.sel.2 = list()
    for(i in 1:5) { 
        spxx.sel.2[[i]] <- projkud2(xx.sel[[i]])
        names(spxx.sel.2)[[i]] <- names(xx.sel)[[i]]
    }
    spxx.sel.303 = list()
    for(i in 1:5) { 
        spxx.sel.303[[i]] <- projkud303(xx.sel[[i]])
        names(spxx.sel.303)[[i]] <- names(xx.sel)[[i]]
    }
    spxx.sel.5 = list()
    for(i in 1:5) { 
        spxx.sel.5[[i]] <- projkud5(xx.sel[[i]])
        names(spxx.sel.5)[[i]] <- names(xx.sel)[[i]]
    }
    spxx.sel.10 = list()
    for(i in 1:5) { 
        spxx.sel.10[[i]] <- projkud10(xx.sel[[i]])
        names(spxx.sel.10)[[i]] <- names(xx.sel)[[i]]
    }
    
    
    spxxg10.list = list(spxx.sel.2, spxx.sel.303, spxx.sel.5, spxx.sel.10)
     names(spxxg10.list) = c("h=2","h=3.03","h=5","h=10")

     
     
    spxx.g2.sel.2 = list()
    for(i in 1:5) { 
        spxx.g2.sel.2[[i]] <- projkud2.g2(xx.sel[[i]])
        names(spxx.g2.sel.2)[[i]] <- names(xx.sel)[[i]]
    }
    spxx.g2.sel.303 = list()
    for(i in 1:5) { 
        spxx.g2.sel.303[[i]] <- projkud303.g2(xx.sel[[i]])
        names(spxx.g2.sel.303)[[i]] <- names(xx.sel)[[i]]
    }
    spxx.g2.sel.5 = list()
    for(i in 1:5) { 
        spxx.g2.sel.5[[i]] <- projkud5.g2(xx.sel[[i]])
        names(spxx.g2.sel.5)[[i]] <- names(xx.sel)[[i]]
    }
    spxx.g2.sel.10 = list()
    for(i in 1:5) { 
        spxx.g2.sel.10[[i]] <- projkud10.g2(xx.sel[[i]])
        names(spxx.g2.sel.10)[[i]] <- names(xx.sel)[[i]]
    }
    
    
    spxxg2.list = list(spxx.g2.sel.2, spxx.g2.sel.303, spxx.g2.sel.5, spxx.g2.sel.10)
     names(spxxg2.list) = c("h=2","h=3.03","h=5","h=10")

```

## Create volume UDs from kernel UDs and plot with contours
```{r}
    windows(); par(mfrow=c(4,5), mar=c(1,1,2,1))
    for(j in 1:4) {
      spxx.sel <- spxxg10.list[[j]]
      for(i in 1:5) {    
            tempxx = spxx.sel[[i]]
            vud = getvolumeUD(tempxx)
            image(vud, main=paste0(names(spxx.sel)[[i]],"sec; ",names(spxxg10.list)[j] ),
                  col=c(heat.colors(6),"white"))
            contour(as.image.SpatialGridDataFrame(vud), add=TRUE, nlevels=6)
      }
    }
     
    windows(); par(mfrow=c(4,5), mar=c(1,1,2,1))
    for(j in 1:4) {
      spxx.g2.sel <- spxxg2.list[[j]]
      for(i in 1:5) {    
            tempxx = spxx.g2.sel[[i]]
            vud = getvolumeUD(tempxx)
            image(vud, main=paste0(names(spxx.g2.sel)[[i]],"sec; ",names(spxxg2.list)[j] ),
                  col=c(heat.colors(6),"white"))
            contour(as.image.SpatialGridDataFrame(vud), add=TRUE, nlevels=6)
      }
    }

```

# Extract cell values from vud / xyz objects
```{r extract grid values}

  cellvalg10.list <- vector("list", 4) 
  for(j in 1:4) {
    cellvalg10.list[[j]] <- vector("list",5)
    for(i in 1:5) {
      gridx.kud = data.frame(cbind(spxxg10.list[[j]][[i]]@coords, spxxg10.list[[j]][[i]]@data$ud))
       names(gridx.kud) <- c("Easting","Northing","UD")
      cellvalg10.list[[j]][[i]] <- gridx.kud
    }
    names(cellvalg10.list[[j]]) <- names(spxxg10.list[[j]])
  }
  names(cellvalg10.list) <- names(spxxg10.list)  
   saveRDS(cellvalg10.list,"DiscSens.RData")
   
  # write each element of the list to a seperate .csv file
   for(j in 1:4) {
   lapply(1:length(cellvalg10.list[[j]]), function(i) write.csv(cellvalg10.list[[j]][[i]], 
                                      file = paste0("DiscSens/grid10_",
                                                    names(cellvalg10.list)[j],"_",
                                                    names(cellvalg10.list[[j]][i]), ".csv"),
                                      row.names = FALSE ) )
   }
  
  # plot one of the lists to test
  testdat = cellvalg10.list[[4]][[5]]
  plot( x= testdat$Easting,  y=testdat$Northing, pch=16,
             col= ifelse(testdat$UD>=.000025,"red","grey90"))
  
  
  
 ## repeat for grid 2  
 cellvalg2.list <- vector("list", 4) 
  for(j in 1:4) {
    cellvalg2.list[[j]] <- vector("list",5)
    for(i in 1:5) {
      gridx.kud = data.frame(cbind(spxxg2.list[[j]][[i]]@coords, spxxg2.list[[j]][[i]]@data$ud))
       names(gridx.kud) <- c("Easting","Northing","UD")
      cellvalg2.list[[j]][[i]] <- gridx.kud
    }
    names(cellvalg2.list[[j]]) <- names(spxxg2.list[[j]])
  }
  names(cellvalg2.list) <- names(spxxg2.list)  
   saveRDS(cellvalg2.list,"DiscSens.RData")
   
  # write each element of the list to a seperate .csv file
   for(j in 1:4) {
   lapply(1:length(cellvalg2.list[[j]]), function(i) write.csv(cellvalg2.list[[j]][[i]], 
                                      file = paste0("DiscSens/grid2_",
                                                    names(cellvalg2.list)[j],"_",
                                                    names(cellvalg2.list[[j]][i]), ".csv"),
                                      row.names = FALSE ) )
   }
  
  # plot one of the lists to test
  testdat = cellvalg2.list[[4]][[5]]
  plot( x= testdat$Easting,  y=testdat$Northing, pch=16,
             col= ifelse(testdat$UD>=.000025,"red","grey90"))
      
```

## try to plot histgrams or other metrics to see how the parameters affect the UDs
```{r}
  png("DiscSens/UTMhist_g10h3t20.png", width=16, height=8, units="in", res=600)
  testdat = cellvalg10.list[[2]][[4]] # h=3.03, 20sec - parameters used in the report
  options(scipen = 999)
  #windows()
  par(mfrow=c(1,2))
  eastsum = summarize(group_by(testdat,Easting), sumUD=sum(UD))
   barplot(eastsum$sumUD, names.arg=eastsum$Easting, las=2, cex.names=.7, main="Grid 10m: h=3.03, t=20s")
   mtext(paste0("Peak at ",eastsum$Easting[eastsum$sumUD==max(eastsum$sumUD)]), side=3, adj=0)
  northsum = summarize(group_by(testdat,Northing), sumUD=sum(UD))
   barplot(northsum$sumUD, names.arg=northsum$Northing, las=2, horiz=TRUE,cex.names=.7)
   mtext(paste0("Peak at ",northsum$Northing[northsum$sumUD==max(northsum$sumUD)]), side=3, adj=1)
    dev.off()

  png("DiscSens/UTMhist_g10h2t22.png", width=16, height=8, units="in", res=600)
  testdat.sm = cellvalg10.list[[1]][[1]] # h=3.03, 20sec - parameters used in the report
  options(scipen = 999)
  #windows()
  par(mfrow=c(1,2))
  eastsum = summarize(group_by(testdat.sm,Easting), sumUD=sum(UD))
   barplot(eastsum$sumUD, names.arg=eastsum$Easting, las=2, cex.names=.7, main="Grid 10m: h=2, t=2s")
   mtext(paste0("Peak at ",eastsum$Easting[eastsum$sumUD==max(eastsum$sumUD)]), side=3, adj=0)
  northsum = summarize(group_by(testdat.sm,Northing), sumUD=sum(UD))
   barplot(northsum$sumUD, names.arg=northsum$Northing, las=2, horiz=TRUE,cex.names=.7)
   mtext(paste0("Peak at ",northsum$Northing[northsum$sumUD==max(northsum$sumUD)]), side=3, adj=1)
    dev.off()

  png("DiscSens/UTMhist_g10h10t30.png", width=16, height=8, units="in", res=600)
  testdat.lg = cellvalg10.list[[4]][[5]] # h=3.03, 20sec - parameters used in the report
  options(scipen = 999)
  #windows()
  par(mfrow=c(1,2))
  eastsum = summarize(group_by(testdat.lg,Easting), sumUD=sum(UD))
   barplot(eastsum$sumUD, names.arg=eastsum$Easting, las=2, cex.names=.7, main="Grid 10m: h=10, t=30s")
   mtext(paste0("Peak at ",eastsum$Easting[eastsum$sumUD==max(eastsum$sumUD)]), side=3, adj=0)
  northsum = summarize(group_by(testdat.lg,Northing), sumUD=sum(UD))
   barplot(northsum$sumUD, names.arg=northsum$Northing, las=2, horiz=TRUE,cex.names=.7)
    mtext(paste0("Peak at ",northsum$Northing[northsum$sumUD==max(northsum$sumUD)]), side=3, adj=1)
   dev.off()

   
   
  png("DiscSens/UTMhist_g2h3t20.png", width=16, height=8, units="in", res=600)
  testdat = cellvalg2.list[[2]][[4]] # h=3.03, 20sec - parameters used in the report
  options(scipen = 999)
  #windows()
  par(mfrow=c(1,2))
  eastsum = summarize(group_by(testdat,Easting), sumUD=sum(UD))
   barplot(eastsum$sumUD, names.arg=eastsum$Easting, las=2, cex.names=.7, main="Grid 2m: h=3.03, t=20s")
   mtext(paste0("Peak at ",eastsum$Easting[eastsum$sumUD==max(eastsum$sumUD)]), side=3, adj=0)
  northsum = summarize(group_by(testdat,Northing), sumUD=sum(UD))
   barplot(northsum$sumUD, names.arg=northsum$Northing, las=2, horiz=TRUE,cex.names=.7)
   mtext(paste0("Peak at ",northsum$Northing[northsum$sumUD==max(northsum$sumUD)]), side=3, adj=1)
    dev.off()

  png("DiscSens/UTMhist_g2h2t2.png", width=16, height=8, units="in", res=600)
  testdat.sm = cellvalg2.list[[1]][[1]] # h=2, 2sec - parameters used in the report
  options(scipen = 999)
  #windows()
  par(mfrow=c(1,2))
  eastsum = summarize(group_by(testdat.sm,Easting), sumUD=sum(UD))
   barplot(eastsum$sumUD, names.arg=eastsum$Easting, las=2, cex.names=.7, main="Grid 2m: h=2, t=2s")
   mtext(paste0("Peak at ",eastsum$Easting[eastsum$sumUD==max(eastsum$sumUD)]), side=3, adj=0)
  northsum = summarize(group_by(testdat.sm,Northing), sumUD=sum(UD))
   barplot(northsum$sumUD, names.arg=northsum$Northing, las=2, horiz=TRUE,cex.names=.7)
   mtext(paste0("Peak at ",northsum$Northing[northsum$sumUD==max(northsum$sumUD)]), side=3, adj=1)
    dev.off()

  png("DiscSens/UTMhist_g2h10t30.png", width=16, height=8, units="in", res=600)
  testdat.lg = cellvalg2.list[[4]][[5]] # h=10, 30sec - parameters used in the report
  options(scipen = 999)
  #windows()
  par(mfrow=c(1,2))
  eastsum = summarize(group_by(testdat.lg,Easting), sumUD=sum(UD))
   barplot(eastsum$sumUD, names.arg=eastsum$Easting, las=2, cex.names=.7, main="Grid 2m: h=10, t=30s")
   mtext(paste0("Peak at ",eastsum$Easting[eastsum$sumUD==max(eastsum$sumUD)]), side=3, adj=0)
  northsum = summarize(group_by(testdat.lg,Northing), sumUD=sum(UD))
   barplot(northsum$sumUD, names.arg=northsum$Northing, las=2, horiz=TRUE,cex.names=.7)
   mtext(paste0("Peak at ",northsum$Northing[northsum$sumUD==max(northsum$sumUD)]), side=3, adj=1)
    dev.off()
   
  png("DiscSens/UTMhist_g2h2t30.png", width=16, height=8, units="in", res=600)
  testdat.mx1 = cellvalg2.list[[1]][[5]] # h=2, 30sec - parameters used in the report
  options(scipen = 999)
  #windows()
  par(mfrow=c(1,2))
  eastsum = summarize(group_by(testdat.mx1,Easting), sumUD=sum(UD))
   barplot(eastsum$sumUD, names.arg=eastsum$Easting, las=2, cex.names=.7, main="Grid 2m: h=2, t=30s")
   mtext(paste0("Peak at ",eastsum$Easting[eastsum$sumUD==max(eastsum$sumUD)]), side=3, adj=0)
  northsum = summarize(group_by(testdat.mx1,Northing), sumUD=sum(UD))
   barplot(northsum$sumUD, names.arg=northsum$Northing, las=2, horiz=TRUE,cex.names=.7)
   mtext(paste0("Peak at ",northsum$Northing[northsum$sumUD==max(northsum$sumUD)]), side=3, adj=1)
    dev.off()
   
  png("DiscSens/UTMhist_g2h10t2.png", width=16, height=8, units="in", res=600)
  testdat.mx2 = cellvalg2.list[[4]][[1]] # h=10, 2sec - parameters used in the report
  options(scipen = 999)
  #windows()
   par(mfrow=c(1,2))
  eastsum = summarize(group_by(testdat.mx2,Easting), sumUD=sum(UD))
   barplot(eastsum$sumUD, names.arg=eastsum$Easting, las=2, cex.names=.7, main="Grid 2m: h=10, t=2s")
   mtext(paste0("Peak at ",eastsum$Easting[eastsum$sumUD==max(eastsum$sumUD)]), side=3, adj=0)
  northsum = summarize(group_by(testdat.mx2,Northing), sumUD=sum(UD))
   barplot(northsum$sumUD, names.arg=northsum$Northing, las=2, horiz=TRUE,cex.names=.7)
   mtext(paste0("Peak at ",northsum$Northing[northsum$sumUD==max(northsum$sumUD)]), side=3, adj=1)
    dev.off()
