---
title: "Rediscretization_Temporal"
author: "Anna Steel"
date: "September 6, 2016"
output: pdf_document
---
```{r, include=FALSE} 
# required packages
library(dplyr)
library(sp)
library(rgdal)
library(rgeos)
library(maptools)
library(ggplot2)
library(grid) 
library(cowplot)
library(viridis)
library(adehabitatLT)
library(adehabitatHR)
#library(userfriendlyscience)

river3 = readOGR("C:/Users/Anna/Documents/GitHub/Fremont16/GIS/2004_channel","2004_channel_freTightclip")

```


## Rediscretization of Tracks - 20 seconds between positions
- Using primary and secondary filtered data to rediscretize tracks for further analysis
- Tracks have been split into bursts where successive positions were seperated by > 50m
* this threshold can be altered in "Final_Filtering.Rmd" if desired
- Before redistretizing, remove bursts with < 10 positions (too few to rediscretize in adehabitatLT)
- also note that the interval of 20 seconds was selected to be consistent with the 2015 analysis; another script will discretize at 2 seconds to be more consitent with ELAM outputs and USGS analysis
```{ r, echo=FALSE }
  options(digits=20) #keep 
  load("Maestros/AllFish_FiltSec4Bursts.RData")  # single object, named red7
 
 dim(red7) # 102633 detections 
    length(unique(red7$id))  # 430 unique fish
    length(unique(red7$burst))  # 588 unique bursts
    
    ndetects.fish = summarize(group_by(red7, id), ndet = n())  
      mean(ndetects.fish$ndet) # 238.9 per fish
      range(ndetects.fish$ndet) # ranges from 28 - 660
    ndetects.burst = summarize(group_by(red7, burst), ndet = n())  
      mean(ndetects.burst$ndet) # 174.5 per fish
      range(ndetects.burst$ndet) # ranges from 3 - 660
      
    max(red7$spd_mps, na.rm=T)  # 86.6 mps
```

```{r}
  bursts.rem = data.frame(ndetects.burst[ndetects.burst$ndet<10,])
     nrow(bursts.rem) # 74 bursts removed
    sum(bursts.rem$ndet) # 373 positions removed
  red.br =  red7[(red7$burst %in% bursts.rem$burst),] 
  
  ggplot(data = red.br, aes(x=east, y=north)) + geom_point() + 
    geom_path(data = river3, aes(long, lat), col="gold", size=1.2 ) +
    ggtitle(label = "Positions Removed within Short Bursts") +
    theme_bw() + coord_fixed()
    
  red8 = red7[!(red7$burst %in% bursts.rem$burst),]

  red8.ltraj = as.ltraj(xy=red8[,c("east","north")], date=red8$date, 
                        id=red8$id, burst = factor(red8$burst),
                        infolocs=red8[,c("Hpes","east","north")])
```

## Discretize in Time
```{r}
  # discretize in time
  red8.trdz = ld(redisltraj(red8.ltraj, u=20, type="time", nnew=50))
   red8.trdz$run = "LFC" # creates a common grouping variable to make UD with all points
   red8.trdz=red8.trdz[order(red8.trdz$id,red8.trdz$date),]
   
 # recalculate migration speed  
   red8.trdz$spd_mps = red8.trdz$dist / red8.trdz$dt
```
```{r, echo=FALSE}

#  # add in extra info when I get it from Jon
#    tagrel = read.csv("DATA/Maestro_tagging_WRC-LFC.csv")
#       tagrel = tagrel[,c("ID.Tag","Species","Time.Date.Release","RelEv","Weight","Fork.Length")] # time in PST
#       names(tagrel) = c("id","run","datetime.Rel","RelEv","Weight","FL")
#        
#       library(plyr)
#        red8.trdz = join(red8.trdz, tagrel, type="left")
#       detach(package:plyr)
#   
#       red8.trdz$RelHr = as.POSIXlt(red8.trdz$datetime.Rel, format="%m/%d/%Y %H:%M")$hour
#       red8.trdz$datetime.Rel = NULL

  ## write this to file
  saveRDS(red8.trdz, "Maestros/RediscTime_20s.RData")
```



And finally, output the general metrics about the remaining dataset
```{r}
    dim(red8.trdz) # 17004 detections after discretization
    length(unique(red8.trdz$id))  # 430
    ndetects.discr = summarize(group_by(red8.trdz, id), ndet = n())  
      mean(ndetects.discr$ndet) # 39.54 per fish
      range(ndetects.discr$ndet) # ranges from 5 - 551
    max(red8.trdz$spd_mps, na.rm=T)  # 2.36 mps
    ```
